---
title: "The Prices of Airbnb Units: An Interactive Document"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

#Dataset Description
This dataset was obtained online from Kaggle.com and contains the nightly prices of Airbnb postings in various major cities across the US. Airbnb is a platform for people to rent out their property for short-term lodging. The dataset contains fields such as the type of property (e.g. apartment, house), room type (e.g. private room, shared room, entire home), city, number of reviews, and various boolean fields to indicate whether or not a listing has a given amenity (e.g. allows pets). By joining with census data found on Data.world, we have also included fields for median age and average income - both by zip code, a field which is present in the original data.

#Important Links

[Data.world Project](https://data.world/brandon-kerbow/s18-edv-project-4)

Kyle's Insights: [1](https://data.world/brandon-kerbow/s18-edv-project-4/insights/c0365682-6ca9-424a-8617-8c80051940ac)
[2](https://data.world/brandon-kerbow/s18-edv-project-4/insights/883d3021-1691-4801-bc1c-064a8d5dac04)

Jeffrey's Insights:
[1](https://data.world/brandon-kerbow/s18-edv-project-4/insights/d4ee2f89-adf9-48f9-a394-96750c428b91)
[2](https://data.world/brandon-kerbow/s18-edv-project-4/insights/1778e3bd-a498-4d75-969b-39edbfae4419)

Brandon's Insights:
[1](https://data.world/brandon-kerbow/s18-edv-project-4/insights/be381f9b-b05f-4558-862b-7e0a38e19110)
[2](https://data.world/brandon-kerbow/s18-edv-project-4/insights/cd77eb59-889f-4b36-b0ec-12df8efb51eb)

Derek's Insights:
[1](https://data.world/brandon-kerbow/s18-edv-project-4/insights/8de30184-b578-4280-ac35-d850460c63aa)
[2](https://data.world/brandon-kerbow/s18-edv-project-4/insights/bf9ebbbd-f4ad-47a4-9cfd-adb4f171be7e)

[Github Repository](https://github.com/CannataUTDV/s18dvproject4-duquesnay-feng-orji-kerbow)

#Motivations and Expectations 
With housing being a hot topic in both business and everyday life, we wanted to explore some drivers for the prices. In the interest of seeing which cities provide the most bang for your buck or which would be ideal for finding an Airbnb, we explore cities which stood out in one way or another. We explore mainly the average price of per night of Airbnb postings by city and apartment price, but also analyze the ratings and median income of areas. 

We would expect that cities which have higher average prices per night have this reflected in all different types of properties. We would also expect that no city has an abnormally high number of low/outlier ratings and that the median income tends to go hand-in-hand with average nightly prices. Lastly, we expected that reviews would be largely negative similar to how reviews of apartment complexes near UT are mostly negative. As we explore in detail in the visuals, however, we will show that these are not always the case. 


#Summary of Conclusions
Through our analysis of the data and visuals in subsequent sections, we found that our expectations were not always correct. Although most cities which had high average prices per night had this reflected across all property types, this was not the case in LA. Additionally, in NYC we observed that the high number of outliers in average nightly price could be explained by the relatively large distribution of income levels in the differing zip codes of the city. This seemed to have an effect on both prices and reviews. Finally, we see that customers were more likely to leave a review if their stay met or exceeded expectations and typically did not leave a review if their expectations weren't met.




```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
source("brandonDataA.R", local = TRUE)
source("brandonDataB.R", local = TRUE)

```
```{r}
source("JeffDataA.R", local = TRUE)
source("JeffDataB.R", local = TRUE)


```

```{r}
projectBrandon <- "https://data.world/brandon-kerbow/s18-edv-project-4" 
data.world::set_config(cfg_env("DW_API")) 
cities <- data.world::query(data.world::qry_sql(
 "   
	select distinct city
	from AirBnBClean
 "), 
dataset = projectBrandon)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
data.world::set_config(cfg_env("DW_API")) 
city <- data.world::query(data.world::qry_sql(
  "   
  select distinct airbnbclean.city from airbnbclean
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
data.world::set_config(cfg_env("DW_API")) 
price <- data.world::query(data.world::qry_sql(
  "   
  select distinct airbnbclean.nightly_price from airbnbclean
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
data.world::set_config(cfg_env("DW_API")) 
propType <- data.world::query(data.world::qry_sql(
  "   
  select distinct airbnbclean.property_type from airbnbclean
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
data.world::set_config(cfg_env("DW_API")) 
income <- data.world::query(data.world::qry_sql(
  "   
  select distinct IRSIncomeByZipCode.avg_total_income from IRSIncomeByZipCode
  "), 
  dataset = project)
```

#Exploring Loft Prices in LA - Bar Charts
This dashboard contains two tabs, both bar charts.  The dashboard - and the subsequent crosstab - explore the price differences of Airbnb postings by city and property type. We would expect that for cities which have higher prices, the higher price is equally represented across all property types. This was, however, found to not always be the case. We show that Los Angeles has disproportionally expensive loft units and explore why this may be so.

The dashboard's input panel allows the user to decide which cities(s) they would like to see present in the data. The slider for average price per night filters which property types are shown for a given city based on whether or not that value falls within the bounds. Note that for these plots, and some others on this document, the text in the legend is quite small. This is to avoid having the legend overlay the plot.

##Tab 1 - Discovering the Abnormally Expensive LA Lofts
The first tab's bar chart shows the average price per night (y-axis) for each city (x-axis) by property type (color). It is immediately clear that Washington D.C. and San Francisco have the most expensive rentals overall, but it is more interesting to compare the different property types across cities. Los Angeles, for example, has the second to shortest stack (i.e. the second cheapest overall rentals) but the second to highest average nightly price for lofts (shown in blue). This indicates that LA has disproportionally expensive lofts, but why is this the case? The visual in the second tab and the subsequent crosstab shed some light on this.

##Tab 2 - Charging Extra for Pets
The second tab's bar chart is filtered to only show lofts and - just like the first tab -  has average price per night and city on the y and x axes, respectively. This plot, however, has the bars colored based on whether or not the loft allows pets. We see that LA, relative to the other cities, has lofts which charge disproportionately more for the luxury of allowing pets. Given that most of the lofts across all cities allow pets, this plays into LA having disproportionally expensive lofts. Though interesting, this is likely not one of the biggest drivers of LA's disproportionally expensive lots. To see a bigger reason for this observation, we direct you to the subsequent crosstab.






```{r}
inputPanel(
  selectInput("selectCity_1", label = "Select City",choices = cities, multiple=TRUE, selected=c
("NYC",
"LA",
"DC",
"SF",
"Chicago",
"Boston")),

  sliderInput("PriceFilter", label = "Average Price per Night:",
              min = 0, max = 400, value = c(0, 400), step = 20)
)
```


```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Price by Property Type", tabName = "barchartBrandon", icon = icon("dashboard")),
      menuItem("Price by Pet Policy", tabName = "barchart2Brandon", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "BarChart2"
      tabItem(tabName = "barchartBrandon",
        p("This is a barchart of City and Average Price per Night, by Property Type"),
        source("brandonbarChart1UI.R",local = TRUE)$value
      ),
       # 2. "BarChart1"
      tabItem(tabName = "barchart2Brandon",
        p("This is a barchart of City and Average Price per Night, by Pet Policy"),
        source("brandonbarChart2UI.R",local = TRUE)$value
      )
    )
  )
)
source("brandonbarChart1Server.R", local = TRUE)
source("brandonbarChart2Server.R", local = TRUE)

```

#Exploring Loft Prices in LA - Crosstab
This crosstab shows the average price per night for lofts by city and type of room. The x and y axes show the city and type of room, respectively. The data within the crosstab shows the average price per night. The colors provide a conditional formatting to make it apparent where the low (blue), medium (green), and hih (red) prices are. Cities can be filtered out with input box and the sliders control the thresholds for being classified as low, medium, and high A value is considered high if it is greater than the "bottom high" value, low if it is smaller than the "top low" value, and medium otherwise (i.e. between these two values).

Similar to the bar charts, we would expect that cities which have more expensive loft prices have this higher price represented equally across all types of lofts. Instead however, we see that lofts which are private rooms are significantly more expensive in LA than any other city, contributing to LA's disproportionately expensive lofts which was observed in the previous dashboard's first tab.

```{r}
inputPanel(
  selectInput("selectCity_2", label = "Select City",
              choices = cities, multiple=TRUE, selected=c
              
  ("NYC","LA","DC","SF","Chicago","Boston")),
              
              
  sliderInput("bottomHigh", label = "Bottom High:",
              min = 200, max = 400, value = 200, step = 10),
  
  sliderInput("topLow", label = "Top Low:",
              min = 60, max = 150, value = 100, step = 5)
)
```


```{r}
dfBrandon <- eventReactive(c(input$selectCity_2, input$bottomHigh, input$topLow), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-4" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
    select cast(avg(nightly_price) as int) as continuous_kpi, city, room_type,
    case 
    when avg(nightly_price) > ? then 'High'
    when avg(nightly_price) < ? then 'Low'
    else 'Medium'
    end as discrete_kpi
    from AirBnBClean s
    where property_type = 'Loft'
    group by city, room_type
    
    --where city in (?, ?, ?, ?, ?, ?)
   ")
  # paramQuery$params <- c(input$bottomHigh, input$topLow, input$selectRegion)
  paramQuery$params <- c(input$bottomHigh, input$topLow)
  data.world::query(paramQuery, dataset = project)
}) 

# The following is needed because  what's in the SQL query above doesn't work if uncommented
df1BrandonCrosstab <- eventReactive(c(input$bottomHigh, input$topLow, input$selectCity_2), { 
  dfBrandon() %>% dplyr::filter(city %in% input$selectCity_2)
})

Cities <- eventReactive(c(input$selectCity_2), { 
  library('stringr')
  str_c(input$selectCity_2, collapse=', ')
})

# Notice the need to use df1() below:
renderDataTable({
  DT::datatable(df1BrandonCrosstab(), rownames = FALSE,
  extensions = list(Responsive = TRUE, FixedHeader = TRUE)
  )
})
```


```{r}
renderPlot({
  df1BrandonCrosstab() %>% ggplot() + geom_text(mapping = aes(x=city, y=room_type, label=continuous_kpi), size=20) +
  geom_tile(aes(x=city, y=room_type, fill=discrete_kpi), alpha=0.50) +
  theme(legend.text=element_text(size=45)) +
  theme(axis.text=element_text(size=45),
        axis.title=element_text(size=45, face="bold"))  + 
  theme(plot.title = element_text(size = 60, face = "bold")) + 
  ggtitle(paste("Average Price per Night, by City and Room Type")) +
  xlab("City") + ylab("Room Type")
}, height = 2000, width = 2000
)
```



```{r}

df1kyle <- eventReactive(c(input$selectPrice_1kyle, input$selectCity_1kyle), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
    "
    select city, nightly_price, property_type
    from airbnbclean h
    where nightly_price between ? and ? and city in (?,?,?,?,?,?) and property_type in ('Apartment','Bed_&_Breakfast', 'Boat', 'Boutique_hotel', 'Bungalow', 'Cabin', 'Camper/RV', 'Castle', 'Condominium', 'Dorm', 'Guest_suite', 'Guesthouse', 'Hostel', 'House', 'In-law', 'Loft', 'Other', 'Serviced_apartment', 'Timeshare', 'Tipi', 'Townhouse', 'Treehouse', 'Villa')
    
    order by city
    "
    )
  paramQuery$params <- c(input$selectPrice_1kyle[1], input$selectPrice_1kyle[2], input$selectCity_1kyle[1], input$selectCity_1kyle[2], input$selectCity_1kyle[3], input$selectCity_1kyle[4], input$selectCity_1kyle[5], input$selectCity_1kyle[6])
  data.world::query(paramQuery, dataset = project)
}) 

```


```{r}

df2kyle <- eventReactive(c(input$selectIncome_2kyle, input$selectCity_1kyle), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-4/" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
    "   
        select * from(
    
    select city, property_type, cast(c.avg_total_income as int) as avg_total_income_for_zipcode
    from airbnbclean a
    LEFT JOIN 
    (SELECT replace(a.zipcode,',','') as zipcode, a.avg_total_income
    FROM irsincomebyzipcode a)c
    
    on a.zipcode = c.zipcode) d
    
   where avg_total_income_for_zipcode  between ? and ? and city in (?,?,?,?,?,?) and property_type in ('Apartment','Bed_&_Breakfast', 'Boat', 'Boutique_hotel', 'Bungalow', 'Cabin', 'Camper/RV', 'Castle', 'Condominium', 'Dorm', 'Guest_suite', 'Guesthouse', 'Hostel', 'House', 'In-law', 'Loft', 'Other', 'Serviced_apartment', 'Timeshare', 'Tipi', 'Townhouse', 'Treehouse', 'Villa')
    
    order by city
    
    

    
    
    ")
  paramQuery$params <- c(input$selectIncome_2kyle[1], input$selectIncome_2kyle[2], input$selectCity_1kyle[1], input$selectCity_1kyle[2], input$selectCity_1kyle[3], input$selectCity_1kyle[4], input$selectCity_1kyle[5], input$selectCity_1kyle[6])
  data.world::query(paramQuery, dataset = project)
}) 

```


```{r}
City <- eventReactive(c(input$selectCity_1kyle), { 
  library('stringr')
  str_c(input$selectCity_1kyle, collapse=', ')
})
```

```{r}
Price <- eventReactive(c(input$selectPrice_1kyle), { 
  library('stringr')
  str_c(input$selectPrice_1kyle, collapse=', ')
})
```

```{r}
City2 <- eventReactive(c(input$selectCity_2kyle), { 
  library('stringr')
  str_c(input$selectCity_1kyle, collapse=', ')
})
```

```{r}
Income <- eventReactive(c(input$selectIncome_2kyle), { 
  library('stringr')
  str_c(input$selectIncome_2kyle, collapse=', ')
})
```

#Exploring Distribution of Prices and Incomes
This dashboard contains two tabs, both boxplots. The dashboard explores the distribution of prices and median incomes within the cities. We would expect that the distributions of the nightly prices and median income tend to look similar for a given city and property type, but we will see that for some cases - specifically houses in NYC - that is not always the case. 

The dashboard's input panel allows the user to decide which cities(s) they would like to see present in the data. The sliders for average price per night and average income filter the data for their tabs (tab one and two, respectively) so that only listings within the specified range of values are shown. 

##Tab 1 - Distribution of Prices
The first tab's bar chart shows the average price per night (y-axis) for each city (x-axis) by property type (color). With all types of properties selected the visuals are a bit cluttered, so it is helpful to filter down to property types of interest. We would like to highlight the selection of "apartment", shown in red. With just apartment selected, we see that NYC has an IQR which is similar to that of other cities, perhaps even a bit on the narrow side. It is also immediately obvious that there are quite a lot of outliers in NYC apartment nightly prices. But what could be causing this? We explore this by observing the median incomes for the zip code which NYC apartments are located. 


##Tab 2 - Distribution of Incomes
The second tab's boxplot - just like the first tab -  has city and apartment type as the x axis and color, respectively. The y axis however, is changed to average income per zip code. A boxplot for a given city and apartment is interpreted as follows: "For a given city, Airbnb listings of a given property type span a number of zip codes. This is the distribution of the average income for those zip codes."

To follow up on our previous tab's analysis, we filter by the property type "apartment" and observe the data for NYC. We see that NYC has a noticeably larger IQR than the other cities, indicating that the apartments which are listed on Airbnb in NYC cover a wide range of zip codes - from very poor to very wealthy areas. This wide spread can help explain the high number of outliers observed in the previous plot of nightly price - as the wealthy areas are often asking for prices well above the median. 



```{r}
inputPanel(
  selectInput("selectCity_1kyle", label = "Select Cities",choices = city, multiple=TRUE, selected=c("Boston", "Chicago", "DC", "LA", "NYC", "SF")
    
  )
  
  ,sliderInput("selectPrice_1kyle", label = "Average Price per Night", min = 0, max = 2000, value = c(0, 2000), step = 5),
  
  sliderInput("selectIncome_2kyle", label = "Average Income", min = 0, max = 1000, value = c(0, 1000), step = 5)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Price per Night by City", tabName = "boxplot1", icon = icon("dashboard1")),
      menuItem("Average Income by Zip Code", tabName = "boxplot2", icon = icon("dashboard1"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Nightly price" tab content
      tabItem(tabName = "boxplot1",
              source("kyleBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Average income per zipcode" tab content
      tabItem(tabName = "boxplot2",
              source("kyleBoxPlot2UI.R",local = TRUE)$value
              )
    )
  )
)

source("kyleBoxPlot1Server.R", local = TRUE)
source("kyleBoxPlot2Server.R", local = TRUE)

```

#Exploring Reviews
This dashboard contains two tabs, a boxplot and a histogram. The dashboard explores the distribution of review score ratings and some possible explanations behind these distributions. We did not expect any city to have a higher or lower number of outliers but we found this not to be the case. Once again we have NYC - with its high number of low reviews - as an example of interest.
The dashboard's input panel allows the user to decide which cities(s) they would like to see present in the data.

##Tab 1 - Distribution of Review Scores
The first tab's bar chart shows the review score ratings (y-axis) for Airbnb postings in a given city (x-axis).  It can be seen that NYC not only has the most variable ratings but also the most outliers. Per our analysis in the previous dashboard, it could be that a wide range of income levels in the city leads to a wide range of review scores. We will explore this further in the next tab.

##Tab 2 - Distribution of Incomes
The second tab is a histogram which shows average total Income (x axis), the count of zip codes which have this average total income (y-axis), colored by city. We see that NYC - shown in dark blue - has a high count across many different income levels. This helps confirm the belief that previous tabs brought to light: NYC has a wide range of incomes, which could play into its wide range of review scores. 

```{r}
inputPanel(
  selectInput("selectCity_1", label = "Select City",choices = cities, multiple=TRUE, selected=c("DC","NYC","LA","SF","Chicago","Boston"))
)
```


```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Ratings by City", tabName = "boxplot", icon = icon("dashboard")),
      menuItem("Average Income by City", tabName = "histogram", icon = icon("dashboard"))
      
      
      
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Histo
      tabItem(tabName = "boxplot",
        p("This is a boxplot of review scores"),
        source("Boxplot1UI.R",local = TRUE)$value
      ),
      # 2. "Boxplot 1
      tabItem(tabName = "histogram",
        p("This is a histogram of average income"),
        source("Histogram2UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram2Server.R", local = TRUE)
source("Boxplot1Server.R", local = TRUE)



```

#Embedded Tableau Insight - Review Ratings
The embedded Tableau insight uses a histogram to visualize the frequency of various review score ratings received at Airbnb sites.

As can be seen, the majority of review scores ratings were between 80 and 100, indicating customer's overall satisfaction with their stays. Review score ratings under 80 were very infrequent. Based upon this finding the following question was posed: were Airbnb customers simply enjoying their stays so much so that it was rare for a bad review score rating to be given, or were customers only inclined to leave a review score rating if their stay was satisfactory?

By coloring the bins of the histogram based on the average number of reviews received by each Airbnb site with the corresponding review score rating, it is evident that sites with higher review score ratings were characterized by a significantly greater number of actual reviews (see legend for color scale). This indicates that customers were more likely to leave a review if their stay met or exceeded expectations and typically declined to leave a review if their expectations weren't met.

<iframe src="https://public.tableau.com/views/FrequencyofReviewScoresRating/HistogramofReviewScoresRatingColoredbyAverageNumberofReviewsperRating??:showVizHome=no"width="800" height="800"></iframe>


#Appendix

##Data Cleaning Code
(Click "code" to your right to see the code)
```{r, eval= FALSE}
csvURL <- "https://query.data.world/s/thloshzuglkm24pueeag4uckcshrss"
df <- read_csv(csvURL)
# Change .+ and -+ in column names to _
names(df) <- gsub("\\.", "_", names(df))
# Remove non-printable characters from column names.
names(df) <- gsub("[^ -~]", "", names(df)) 

# Change dashes in columns to unknowns, and dashes in close_amount to 0's
df$log_price <- gsub("^\s*", "0", df$log_price)
df$property_type <- gsub("^\s$", "Unknown", df$property_type)
df$room_type <- gsub("^\s$", "Unknown", df$room_type)

# Remove non-printable characters from all column values.
df <- df %>% dplyr::mutate_all(funs(gsub(pattern="[^ -~]", replacement= "", .)))
# The following write_csv followed immediately by a read_csv, fixes the column types.
write_csv(df, "/Users/derekorji/Documents/BNBtemp.csv") # /Users/pcannata/Downloads needs to be changed to a known folder on your machine.
df <- read_csv("/Users/derekorji/Documents/BNBtemp.csv")
# Now save the cleaned data to new.csv
write_csv(df, "/Users/derekorji/Documents/BNB.csv")
# Now load /tmp/new.csv into a data.world Dataset.

```

##SessionInfo

```{r}
sessionInfo()
```

