---
title: "Top Hat Boxplots"
author: "Brandon Kerbow"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
#runs the libraries
```{r setup, include=FALSE}
library(tidyverse)
library(data.world)
library(DT)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#uses the .rEnviron to get this file outto authenticate 
#then it uses SQL code to get he region from the data set
```{r}
project <- "https://data.world/cannata/tophatsuperstore" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from superstore 
 "), 
dataset = project)
```

#the input panel corrosponds to the slider
#if you loo at the GUI you can figure out what corrpsonds to what
#IF YOU MAKE ANOTHER SELECTINPUT THEN YOU MUST USE A NAME OTHE THAN selectRegion
```{r}
inputPanel(
  selectInput("selectRegion", label = "Select Region",
              choices = regions, multiple=TRUE, selected=c("East", "West", "Central", "South")),
  sliderInput("salesFilter", label = "Sales:",
              min = 0, max = 100200, value = c(0, 100200), step = 100)
)
```
#eventReactive is a function that tells it "if any of those things on the panel change"
#then re-run the code below. so everything you change something on the panel, this code
#will change. which makes sense because if we change the slider we want to re-run the query


#then the SQL says we want four columns from the superstore data....
#what do the ? come from? they com from the panel (the UI),
#and as you see below they are called inputSalesFiler1 and inputSalesFilter2
#and we want regeion to be whatever we selected above i.e. what we selected in the UI
#so the question marks get filled in the panel, and the functon paramQueryparams
#fills those ? in based on the panel. This is called a parmeratized (has ? marks)
#SQL query. then the question marks 

#and the results of this query went into df....what went info df is the output
#of an event reative....which is not a dataframe. what eventReactive returns
#is a functon. this function must be called to return the dataframes.

```{r}

df <- eventReactive(c(input$selectRegion, input$salesFilter), { 
  project <- "https://data.world/cannata/tophatsuperstore" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select region, category, sales, order_date
  	from superstore s
    where sales between ? and ? and region in (?, ?, ?, ?)
order by region
   ")
  paramQuery$params <- c(input$salesFilter[1], input$salesFilter[2], input$selectRegion[1], input$selectRegion[2], input$selectRegion[3], input$selectRegion[4])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
Regions <- eventReactive(c(input$selectRegion), { 
  library('stringr')
  str_c(input$selectRegion, collapse=', ')
})
```
#you can loo up renderTable on the shiny cheat sheet
#then we pipe it with a function called dplyr but then we add another column
#called quarter with the code from "Daplr" to (order_date))
```{r}
# Notice the need to use df1() below:
renderDataTable({
  DT::datatable(df() %>% dplyr::mutate(quarter = lubridate::quarter(order_date)), rownames = FALSE,
  extensions = list(Responsive = TRUE, FixedHeader = TRUE)
  )
})
```

```{r}
# Notice the need to use df(), and Regions() below:
renderPlot({
  plot = df() %>% ggplot() + geom_boxplot(mapping = aes(x=category, y=sales, colour = region), size = 2) +
    theme(legend.text=element_text(size=30)) +
    theme(legend.title=element_text(size=40)) + 
    theme(axis.text=element_text(size=30),
          axis.title=element_text(size=30, face="bold")) + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))  + 
    theme(plot.title = element_text(size = 40, face = "bold")) + 
    ggtitle(paste("Sales for", Regions(), " Region(s)")) +
    xlab("Category") + ylab("Sales")
  #ggplotly(plot, tooltip = c("sales"), session="knitr")
  plot
}, height = 2000, width = 2000)
```

```{r}
inputPanel(
  textInput("title", "Title", "Region Sales"),
  textInput("xTitle", "xTitle", "Quarter"),
  textInput("yTitle", "yTitle", "Sales"),
  numericInput("titleFont", "titleFont:", 60),
  numericInput("textFont", "textFont:", 40),
  numericInput("yMin", "yMin:", 0),
  numericInput("yMax", "yMax:", 50000)
)
```

```{r}
df1 <- eventReactive(c(input$selectRegion, input$title, input$titleFont, input$textFont, input$xTitle, input$yTitle, input$yMin, input$yMax), { 
  df() %>% dplyr::filter(between(sales, input$yMin, input$yMax))
})
```

```{r}
# Boxplot - see http://ggplot2.tidyverse.org/reference/geom_boxplot.html
# Notice the need to use df(), and Regions() below:
renderPlot({
  plot = df1() %>% ggplot() + 
    geom_boxplot(mapping = aes(x = as.factor(paste(lubridate::year(order_date),"_",lubridate::quarter(order_date))), y=sales, colour = region), size = 2) +
    
    theme(legend.text=element_text(size=input$textFont),
      legend.title=element_text(size=input$titleFont), 
      legend.key = element_rect(size = 5),
      legend.key.size = unit(5, 'lines')) +
    theme(axis.text=element_text(size=input$textFont),
          axis.title=element_text(size=input$textFont, face="bold")) + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))  + 
    theme(plot.title = element_text(size = input$titleFont, face = "bold")) + 
    ggtitle(paste(Regions(), input$title)) +
    xlab(input$xTitle) + ylab(input$yTitle)
  #ggplotly(plot, tooltip = c("sales"), session="knitr")
  plot
}, height = 2000, width = 2000)
```
