---
title: "TSA Claims Data: An Interactive Document"
author: "Kyle DuQuesnay, Jeffrey Feng, Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

#Introduction
Our Dataset comes from the United States Department of Homeland Security and shows TSA data over claims from airlines around the globe. Fields of particular interest include the airline, type of claim, item category, incident date, disposition, and close amount.

#Important Links: Data.World Project & Insights
Project: [link](https://data.world/derek-orji/s-18-edv-project-1)

Kyle DuQuesnay's insights:
[1](https://data.world/derek-orji/s-18-edv-project-1/insights/81cd8a71-9457-449e-b99c-6dfac2546cab)
[2](https://data.world/derek-orji/s-18-edv-project-1/insights/8f193fe5-3c1c-4c61-93e2-bdbf85eca4fd)

Jeffrey Feng's insights:
[1](https://data.world/derek-orji/s-18-edv-project-1/insights/707c50dd-fdad-4db9-afc5-b13f960d0d8e)
[2](https://data.world/derek-orji/s-18-edv-project-1/insights/c5c17102-8410-44ef-8513-9eb64fe4f57e)

Brandon Kerbow's insights:
[1](https://data.world/derek-orji/s-18-edv-project-1/insights/cb6893e7-839d-4c7d-a7ae-e403bc1c3f66)
[2](https://data.world/derek-orji/s-18-edv-project-1/insights/ea9b67ab-fc4d-47aa-a1eb-2be1b94833e2)

Derek Orji's insights:
[1](https://data.world/derek-orji/s-18-edv-project-1/insights/0b3d3d3c-440a-4edc-89cf-7312c8a80a02)
[2](https://data.world/derek-orji/s-18-edv-project-1/insights/ff849a96-91ff-4369-943c-10e4f3bea41e)



```{r setup, include=FALSE}

#RELATIONSHIP BETWEEN CANATTAS VARIABLES AND OURS, respectively
#regions : Airlines
#selectRegion_1: selectAirline
#Select Region: Select Airline
#salesFilter_1: closeAmountFilter
#Regions: airlines
#sales: close_amount
#region: airline_name

library(tidyverse)
library(data.world)
library(DT)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
project <- "https://data.world/derek-orji/s-18-edv-project-1" 
data.world::set_config(cfg_env("DW_API")) 
Airlines <- data.world::query(data.world::qry_sql(
 "   
	select distinct claimsnew.airline_name 
	from claimsnew 
 "), 
dataset = project)
```


```{r}
project <- "https://data.world/derek-orji/s-18-edv-project-1" 
data.world::set_config(cfg_env("DW_API")) 
itemcategory <- data.world::query(data.world::qry_sql(
 "   
	select distinct claimsnew.item_category 
	from claimsnew 
 "), 
dataset = project)
```

#Select the Airlines and Close Amount range of interest
```{r}
inputPanel(
  selectInput("selectAirline", label = "Select Airline",
              choices = Airlines, multiple=TRUE, 
              selected=c("airline_name",
"Southwest Airlines",
"Delta Air Lines",
"American Airlines",
"UAL",
"USAir",
"Jet Blue",
"Alaska Airlines",
"Spirit Airlines",
"Frontier Airlines"
)),
  sliderInput("CloseAmountFilter", label = "Close Amount:",
              min = 0, max = 5403, value = c(0, 100200), step = 10)
)
```




```{r}

df <- eventReactive(c(input$selectAirline, input$CloseAmountFilter), { 
  project <- "https://data.world/derek-orji/s-18-edv-project-1" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select c.claim_number, c.airline_name, c.close_amount, c.incident_d, c.item_category
  	from claimsnew c
    where c.close_amount between ? and ? and c.airline_name in

(?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)

order by c.airline_name
   ")
  paramQuery$params <- c(input$CloseAmountFilter[1], input$CloseAmountFilter[2], input$selectAirline[1], input$selectAirline[2], input$selectAirline[3], input$selectAirline[4], input$selectAirline[5], input$selectAirline[6], input$selectAirline[7], input$selectAirline[8], input$selectAirline[9], input$selectAirline[10], input$selectAirline[11], input$selectAirline[12], input$selectAirline[13], input$selectAirline[14], input$selectAirline[15], input$selectAirline[16], input$selectAirline[17], input$selectAirline[18], input$selectAirline[19], input$selectAirline[20], input$selectAirline[21], input$selectAirline[22], input$selectAirline[23], input$selectAirline[24], input$selectAirline[25], input$selectAirline[26], input$selectAirline[27], input$selectAirline[28], input$selectAirline[29], input$selectAirline[30], input$selectAirline[31], input$selectAirline[32], input$selectAirline[33], input$selectAirline[34], input$selectAirline[35], input$selectAirline[36], input$selectAirline[37], input$selectAirline[38], input$selectAirline[39], input$selectAirline[40], input$selectAirline[41], input$selectAirline[42], input$selectAirline[43], input$selectAirline[44], input$selectAirline[45], input$selectAirline[46], input$selectAirline[47], input$selectAirline[48], input$selectAirline[49], input$selectAirline[50], input$selectAirline[51], input$selectAirline[52], input$selectAirline[53], input$selectAirline[54], input$selectAirline[55], input$selectAirline[56], input$selectAirline[57], input$selectAirline[58], input$selectAirline[59], input$selectAirline[60], input$selectAirline[61], input$selectAirline[62], input$selectAirline[63], input$selectAirline[64], input$selectAirline[65], input$selectAirline[66], input$selectAirline[67], input$selectAirline[68], input$selectAirline[69], input$selectAirline[70], input$selectAirline[71], input$selectAirline[72], input$selectAirline[73], input$selectAirline[74], input$selectAirline[75], input$selectAirline[76], input$selectAirline[77], input$selectAirline[78], input$selectAirline[79], input$selectAirline[80], input$selectAirline[81], input$selectAirline[82], input$selectAirline[83], input$selectAirline[84], input$selectAirline[85], input$selectAirline[86], input$selectAirline[87], input$selectAirline[88], input$selectAirline[89], input$selectAirline[90], input$selectAirline[91], input$selectAirline[92], input$selectAirline[93], input$selectAirline[94], input$selectAirline[95], input$selectAirline[96], input$selectAirline[97], input$selectAirline[98], input$selectAirline[99], input$selectAirline[100], input$selectAirline[101], input$selectAirline[102], input$selectAirline[103], input$selectAirline[104], input$selectAirline[105], input$selectAirline[106], input$selectAirline[107], input$selectAirline[108], input$selectAirline[109], input$selectAirline[110], input$selectAirline[111], input$selectAirline[112], input$selectAirline[113], input$selectAirline[114], input$selectAirline[115], input$selectAirline[116], input$selectAirline[117])
  data.world::query(paramQuery, dataset = project)
}) 
```




```{r}
airlines <- eventReactive(c(input$selectAirline), { 
 library('stringr')
  str_c(input$selectAirline, collapse=', ')
})
```

#Data table to retrieve information on selected Airlines based on Close Amount

This interactive table allows the user to retrieve data on airlines selected from the panel above. The sliding scale in the aforementioned panel allows the data to be filtered by close amount. The table displays the airline name, close amount, incident date, item category, and claim number for each claim filed.




```{r}
 #Notice the need to use df1() below:
renderDataTable({
  
  DT::datatable(df(), rownames = FALSE, 
  extensions = list(Responsive = TRUE, FixedHeader = TRUE)
  )
})
```

#Boxplots - Close Amount vs. Airlines


```{r}
tabsetPanel( 
  tabPanel("Settings:"),# To create a tab panel - see https://shiny.rstudio.com/reference/shiny/latest/tabPanel.html
  tabPanel("Plot Size", 
    numericInput("plotWidth_1", "Plot Width:", 800),
    numericInput("plotHeight_1", "Plot Height:", 600)),
  tabPanel("Plot Title",
    textInput("title_1", "Title", "Close Amount vs. Airline"),
    numericInput("titleFont_1", "Title Font", 10)), 
  tabPanel("Plot Legend",
    numericInput("legendTitleSize_1", "Legend Title Size", 10),
    numericInput("legendItemSize_1", "Legend Item Size", 10),
    numericInput("legendKeySize_1", "Legend Key Size", 5)), 
  tabPanel("Axis Labels",
    textInput("xLabel_1", "x-Axis Label", "Airline"),
    textInput("yLabel_1", "y-Axis Label", "Close Amount"),
    numericInput("textFont_1", "textFont:", 10)),
  tabPanel("Data Size", 
    numericInput("yDataMin_1", "yData Minimum (Required):", NA),
    numericInput("yDataMax_1", "yData Maximum (Required):", NA)))
```


```{r}
df1 <- eventReactive(c(input$selectAirline, input$yDataMin_1, input$yDataMax_1), { 
  if( ! is.na(input$yDataMin_1) & ! is.na(input$yDataMax_1)) {
    df() %>% dplyr::filter(between(close_amount, input$yDataMin_1, input$yDataMax_1))
  }
  else {
    df()
  }
})
```





```{r}
# Boxplot - see http://ggplot2.tidyverse.org/reference/geom_boxplot.html
# Notice the need to use df(), and Regions() below:
renderPlotly({
  plot = df1() %>% ggplot() + 
    geom_boxplot(mapping = aes(x = airline_name, y=close_amount, colour = airline_name)) +
     
    theme(plot.title = element_text(size = input$titleFont_1, face = "bold")) + 
    theme( # Legend Attributes - see https://github.com/tidyverse/ggplot2/wiki/Legend-Attributes
      legend.title=element_text(size=input$legendTitleSize_1), 
      legend.text=element_text(size=input$legendItemSize_1),
      legend.key = element_rect(size = input$legendKeySize_1),
      legend.key.size = unit(input$legendKeySize_1, 'lines')) +
    theme(axis.text=element_text(size=input$textFont_1),
          axis.title=element_text(size=input$textFont_1, face="bold"),
          axis.text.x = element_text(angle = 90, hjust = 1))  +
    theme(plot.margin=unit(c(2,1,1,1),"cm")) +
    scale_y_continuous(labels = scales::comma) + # Disable scientific notation
    ggtitle(input$title_1) +
    xlab(input$xLabel_1) + ylab(input$yLabel_1)
  ggplotly(plot, tooltip = c("closeAmount"), session="knitr", width = input$plotWidth_1, height = input$plotHeight_1)
})
```

```{r}
inputPanel( 
  textInput("dummy_2", "", "")
  )
```

```{r}
inputPanel( 
  textInput("dummy_2", "", "")
  )
```





#Boxplots - Close Amount vs. Airline over time

```{r}
tabsetPanel( 
  tabPanel("Settings:"),# To create a tab panel - see https://shiny.rstudio.com/reference/shiny/latest/tabPanel.html
  tabPanel("Plot Size", 
    numericInput("plotWidth_2", "Plot Width:", 800),
    numericInput("plotHeight_2", "Plot Height:", 600)),
  tabPanel("Plot Title",
    textInput("title_2", "Title", "Close Amount vs. Airline"),
    numericInput("titleFont_2", "Title Font", 10)), 
  tabPanel("Plot Legend",
    numericInput("legendTitleSize_2", "Legend Title Size", 10),
    numericInput("legendItemSize_2", "Legend Item Size", 10),
    numericInput("legendKeySize_2", "Legend Key Size", 5)), 
  tabPanel("Axis Labels",
    textInput("xLabel_2", "x-Axis Label", "Date of Claim"),
    textInput("yLabel_2", "y-Axis Label", "Close Amount"),
    numericInput("textFont_2", "textFont:", 10)),
  tabPanel("Data Size", 
    numericInput("yDataMin_2", "yData Minimum (Required):", NA),
    numericInput("yDataMax_2", "yData Maximum (Required):", NA)))
```

```{r}
df2 <- eventReactive(c(input$selectAirline, input$yDataMin_2, input$yDataMax_2), { 
  if( ! is.na(input$yDataMin_2) & ! is.na(input$yDataMax_2)) {
    df() %>% dplyr::filter(between(close_amount, input$yDataMin_2, input$yDataMax_2))
  }
  else {
    df()
  }
})
```

```{r}
# Boxplot - see http://ggplot2.tidyverse.org/reference/geom_boxplot.html
# Notice the need to use df(), and Regions() below:
renderPlotly({
  plot = df2() %>% ggplot() + 
    geom_boxplot(mapping = aes(x = as.factor(paste(lubridate::year(incident_d),"_",lubridate::quarter(incident_d))), y=close_amount, colour = airline_name)) +
     
    theme(plot.title = element_text(size = input$titleFont_2, face = "bold")) + 
    theme( # Legend Attributes - see https://github.com/tidyverse/ggplot2/wiki/Legend-Attributes
      legend.title=element_text(size=input$legendTitleSize_2), 
      legend.text=element_text(size=input$legendItemSize_2),
      legend.key = element_rect(size = input$legendKeySize_2),
      legend.key.size = unit(input$legendKeySize_2, 'lines')) +
    theme(axis.text=element_text(size=input$textFont_2),
          axis.title=element_text(size=input$textFont_2, face="bold"),
          axis.text.x = element_text(angle = 90, hjust = 1))  +
    theme(plot.margin=unit(c(2,1,1,1),"cm")) +
    scale_y_continuous(labels = scales::comma) + # Disable scientific notation
    ggtitle( input$title_2)+
    xlab(input$xLabel_2) + ylab(input$yLabel_2)
  ggplotly(plot, tooltip = c("sales"), session="knitr", width = input$plotWidth_2, height = input$plotHeight_2)
})
```

```{r}
inputPanel( 
  textInput("dummy_2", "", "")
  )
```

```{r}
inputPanel( 
  textInput("dummy_2", "", "")
  )
```

```{r}
inputPanel( 
  textInput("dummy_2", "", "")
  )
```

#Select the Item Category and Close Amount range of interest
```{r}
inputPanel(
  selectInput("selectitemcategory", label = "Select Item Category",
              choices = itemcategory, multiple=TRUE, 
              selected=c("item_category",
"Baggage/Cases/Purses",
"Computer & Accessories",
"Clothing",
"Other"
)))
```
Please only select from amongst the first 120 item categories. Selecting past this will render the histogram useless due to data convolution. 

The following plot is a histogram with a bin size of $200 for close amounts. Shown in different colors are the various item categories which you can add or remove with the input panel. The resulting plot should show the splits by item category within each bin.  Within our data, the five categories with the largest number of claims are Travel Accessories, Personal Electronics, Medical/Science, Jewelry & Watches, and Cosmetics & Grooming. If you change the categories to the listed five, the resulting plot should reveal the majority of claims are within $200. However, the histogram should also reveal that of the claims within $200-$400, personal electronics make up a large section. In addition, a large portion of each bin, especially within the larger bins, is made up by cosmetics and grooming, so it suggests the importance people place on any dollar amount of their cosmetics.
```{r}

DF <- eventReactive(c(input$selectitemcategory, input$CloseAmountFilter), { 
  project <- "https://data.world/derek-orji/s-18-edv-project-1" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select c.close_amount, c.item_category
  	from claimsnew c
    where c.close_amount between ? and ? and c.item_category in

(?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)

order by c.item_category
   ")
  paramQuery$params <- c(input$CloseAmountFilter[1], input$CloseAmountFilter[2], input$selectitemcategory[1], input$selectitemcategory[2], input$selectitemcategory[3], input$selectitemcategory[4], input$selectitemcategory[5], input$selectitemcategory[6], input$selectitemcategory[7], input$selectitemcategory[8], input$selectitemcategory[9], input$selectitemcategory[10], input$selectitemcategory[11], input$selectitemcategory[12], input$selectitemcategory[13], input$selectitemcategory[14], input$selectitemcategory[15], input$selectitemcategory[16], input$selectitemcategory[17], input$selectitemcategory[18], input$selectitemcategory[19], input$selectitemcategory[20],
input$selectitemcategory[21], input$selectitemcategory[22], input$selectitemcategory[23], input$selectitemcategory[24], input$selectitemcategory[25], input$selectitemcategory[26], input$selectitemcategory[27], input$selectitemcategory[28], input$selectitemcategory[29], input$selectitemcategory[30], input$selectitemcategory[31], input$selectitemcategory[32], input$selectitemcategory[33], input$selectitemcategory[34], input$selectitemcategory[35], input$selectitemcategory[36], input$selectitemcategory[37], input$selectitemcategory[38], input$selectitemcategory[39], input$selectitemcategory[40], input$selectitemcategory[41], input$selectitemcategory[42], input$selectitemcategory[43], input$selectitemcategory[44], input$selectitemcategory[45], input$selectitemcategory[46], input$selectitemcategory[47], input$selectitemcategory[48], input$selectitemcategory[49], input$selectitemcategory[50], input$selectitemcategory[51], input$selectitemcategory[52], input$selectitemcategory[53], input$selectitemcategory[54], input$selectitemcategory[55], input$selectitemcategory[56], input$selectitemcategory[57], input$selectitemcategory[58], input$selectitemcategory[59], input$selectitemcategory[60], input$selectitemcategory[61], input$selectitemcategory[62], input$selectitemcategory[63], input$selectitemcategory[64], input$selectitemcategory[65], input$selectitemcategory[66], input$selectitemcategory[67], input$selectitemcategory[68], input$selectitemcategory[69], input$selectitemcategory[70], input$selectitemcategory[71], input$selectitemcategory[72], input$selectitemcategory[73], input$selectitemcategory[74], input$selectitemcategory[75], input$selectitemcategory[76], input$selectitemcategory[77], input$selectitemcategory[78], input$selectitemcategory[79], input$selectitemcategory[80], input$selectitemcategory[81], input$selectitemcategory[82], input$selectitemcategory[83], input$selectitemcategory[84], input$selectitemcategory[85], input$selectitemcategory[86], input$selectitemcategory[87], input$selectitemcategory[88], input$selectitemcategory[89], input$selectitemcategory[90], input$selectitemcategory[91], input$selectitemcategory[92], input$selectitemcategory[93], input$selectitemcategory[94], input$selectitemcategory[95], input$selectitemcategory[96], input$selectitemcategory[97], input$selectitemcategory[98], input$selectitemcategory[99], input$selectitemcategory[100], input$selectitemcategory[101], input$selectitemcategory[102], input$selectitemcategory[103], input$selectitemcategory[104], input$selectitemcategory[105], input$selectitemcategory[106], input$selectitemcategory[107], input$selectitemcategory[108], input$selectitemcategory[109], input$selectitemcategory[110], input$selectitemcategory[111], input$selectitemcategory[112], input$selectitemcategory[113], input$selectitemcategory[114], input$selectitemcategory[115], input$selectitemcategory[116], input$selectitemcategory[117], input$selectitemcategory[118], input$selectitemcategory[119], input$selectitemcategory[120])
  data.world::query(paramQuery, dataset = project)
}) 
```




```{r}
Itemcategory <- eventReactive(c(input$selectitemcategory), { 
 library('stringr')
  str_c(input$selectitemcategory, collapse=', ')
})
```


```{r}
# Notice the need to use DF(), and Itemcategory() below:
renderPlot({
  plot = DF() %>% ggplot() + 
    geom_histogram(mapping = aes(x=close_amount, colour = item_category, fill = item_category), binwidth = 200, size = 2) +
    scale_x_continuous(breaks = seq(0,5000,200)) +
    theme(legend.text=element_text(size=10)) +
    theme(legend.title=element_text(size=10)) + 
    theme(axis.text=element_text(size=10),
          axis.title=element_text(size=10, face="bold")) + 
    theme(axis.text.x = element_text(angle = 10, hjust = 1))  + 
    theme(plot.title = element_text(size = 20, face = "bold")) + 
    ggtitle(paste("Close Amount for", Itemcategory(), " Item Category(s)")) +
    xlab("Close Amount $ (bin)") + ylab("Count of Close Amount")
  #ggplotly(plot, tooltip = c("closeamount"), session="knitr")
  plot
}, height = 600, width = 800)
```

