---
title: "WHO Histogram"
author: "Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

Here's what's loaded:  
library(tidyverse)  
library(shiny)  
library(grid)  
library(data.world)  
library(DT)  
library(shinydashboard)  
library(plotly)  
library(lubridate)  

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(dwapi)
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```



#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("derekDataA.R", local = TRUE)
source("derekDataB.R", local = TRUE)

```


#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
projectDerek <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = projectDerek)
```

```{r}
projectDerek <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
places <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = projectDerek)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Regions <- eventReactive(c(input$selectRegionDerek_1), { 
  library('stringr')
  str_c(input$selectRegionDerek_1, collapse=', ')
})
```

```{r}
Reg <- eventReactive(c(input$selectReg_1), { 
  library('stringr')
  str_c(input$selectReg_1, collapse=', ')
})
```






#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting regions (notice - choices is set to the regions variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectRegionDerek_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA")),
  sliderInput("PopFilter_1", label = "Population Proportion Under 15:", min = 0, max = 100, value = c(0, 100), step = 1)
)
```

```{r}
inputPanel(
  selectInput("selectReg_1", label = "Select Region",choices = places, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("incomeFilter_1", label = "Gross National Income Per Capita:", min = 0, max = 60870, value = c(0, 60870), step = 100)
)
```





#Render and Display the BoxPlots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Category Sales BoxPlot", tabName = "boxplot1", icon = icon("dashboard")),
      menuItem("Quarter Sales BoxPlot", tabName = "boxplot2", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Category Sales BoxPlot" tab content
      tabItem(tabName = "boxplot1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("derekBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Quarter Sales BoxPlot" tab content
      tabItem(tabName = "boxplot2",
        p("And here."),
        source("derekBoxPlot2UI.R",local = TRUE)$value
        )
      )
    )
  )


source("derekBoxPlot1Server.R", local = TRUE)
source("derekBoxPlot2Server.R", local = TRUE)
```

##Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

##Data Cleaning Code.
To be addressed in the next Chapter.
