---
title: "WHO Histogram"
author: "Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

Here's what's loaded:  
library(tidyverse)  
library(shiny)  
library(grid)  
library(data.world)  
library(DT)  
library(shinydashboard)  
library(plotly)  
library(lubridate)  

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(dwapi)
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```



#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("derekDataA.R", local = TRUE)
source("derekDataB.R", local = TRUE)
source("derekDataC.R", local = TRUE)
```


#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
places <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
areas <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Regions <- eventReactive(c(input$selectRegion_1derek), { 
  library('stringr')
  str_c(input$selectRegion_1derek, collapse=', ')
})
```

```{r}
Reg <- eventReactive(c(input$selectReg_1), { 
  library('stringr')
  str_c(input$selectReg_1, collapse=', ')
})
```

```{r}
Re <- eventReactive(c(input$selectRegi_1), { 
  library('stringr')
  str_c(input$selectRegi_1, collapse=', ')
})
```





#Population Proportion, Age Dependency Ratio, and Gross National Income per Capita

According to The Fund for Peace and Foreign Policy, population proportion under 15 years of age is a measure that can serve as an indication of a failed state. In looking at World Health Organization data across world regions, it can be observed that Sub-Saharan African countries constitute a notably large portion of those countries with over 25% of their  population under 15 years of age. This can be seen in the “Population Proportion Under 15 years of Age” Histogram below.  In exploring how population proportion under 15 years of age affects the average country in a region, two measures, Age Dependency Ratio and Gross National Income per Capita, were examined.

Age Dependency Ratio (DR) is an indicator calculated by summing the population under 15 years of age with the population over 65 years of age, and then dividing this sum by the population between ages 15 and 64 (the “productive” age group). DR essentially communicates the number of dependents that each “productive” member of society must provide for. It has many implications for the performance of national economies. The “Age Dependency Ratio” Bar Chart below shows that on average Sub-Saharan African countries have very high DR ratios. Sub-Saharan African countries displayed an average DR ratio of 0.89, much higher than the next highest ratio of 0.62, held by Western European countries (much more economically developed). The fact that a region so underdeveloped has such a relatively small amount of their population contributing to their national economy does not portend well for them. In short, a high DR ratio means that a small portion of a country’s population is contributing to economic output, and bolstering many dependents. How far could this output be going? This idea was further explored through Gross National Income per Capita. 

Gross National Income per Capita is a country’s total income in a year divided by its population. It measures the average income of citizens in a country. The results for Gross National Income per Capita were not surprising for Sub-Saharan African Countries on average. The “Gross National Income per Capita” Boxplot below shows that Sub-Saharan African Countries had the lowest average incomes, with the lowest minimum, first quartile, median, third quartile, and maximum average incomes. This observation goes hand in hand with their low DR ratio, and thus isn’t profound. Obviously, with such a small portion of their population producing economically, the national aggregate income is being allocated over an excess of unproductive citizens, thus yielding a low Gross National Income per Capita. 

Surprisingly (and maybe counterintuitively), although Western European countries recorded the second highest DR ratio, they also had the second highest Gross National Income per Capita. This is striking as it would be expected that they suffer the difficulties of having such a large portion of unproductive citizens. The key to this is in realizing that Western European countries are amongst the most technologically, economically, and socially advanced, especially under western criteria. Because of this, the relatively small portion of productive people in the region can produce economic output that surpasses that from other regions. The same cannot be said for the still developing Sub-Saharan African countries. 


```{r}
inputPanel(
  selectInput("selectRegion_1derek", label = "Select Region for Population Proportion Under 15 years",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
  sliderInput("PopFilter_1", label = "Population Proportion Under 15:", min = 0, max = 100, value = c(0, 100), step = 1),
  selectInput("selectRegi_1", label = "Select Region for Age Dependency Ratio",choices = places, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA"))
)
```

```{r}
inputPanel(
  selectInput("selectReg_1", label = "Select Region for Gross National Income",choices = areas, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("incomeFilter_1", label = "Gross National Income Per Capita:", min = 0, max = 60870, value = c(0, 60870), step = 100)
)
```




#Render and Display the BoxPlots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Population Proportion Under 15 years Histogram", tabName = "Histo1", icon = icon("dashboard")),
      menuItem("Age Dependency Ratio Barchart", tabName = "barchart1", icon = icon("dashboard")),
      menuItem("Gross National Income per Capita Boxplot", tabName = "boxplot", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Population Proportion Under 15 years Histogram" tab content
      tabItem(tabName = "Histo1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("derekBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Dependent Ratio Barchart" tab content
      tabItem(tabName = "barchart1",
        p("And here."),
        source("derekbarChart2UI.R",local = TRUE)$value
        ),
      # 3. "Gross National Income per Capita Boxplot" tab content
      tabItem(tabName = "boxplot",
        p("And here."),
        source("derekBoxPlot2UI.R",local = TRUE)$value
        )
      )
    )
  )


source("derekBoxPlot1Server.R", local = TRUE)
source("derekbarChart2Server.R", local = TRUE)
source("derekBoxPlot2Server.R", local = TRUE)
```

##Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

##Data Cleaning Code.
To be addressed in the next Chapter.
