---
title: "WHO Data"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, Brandon's portion of project 3. 

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(leaflet)
knitr::opts_chunk$set(echo = TRUE)
```

#Tableau Link



```{r}
source("brandonsDataA.R", local = TRUE)
source("brandonsDataB.R", local = TRUE)
source("brandonsDataC.R", local = TRUE)
```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
systemsOfGovernment <- data.world::query(data.world::qry_sql(
 "   
	select distinct system_of_government from who_cleanest

 "), 
dataset = project)
```

#Create a System of Government Variable
Create a System of Government variable with a string constructed from the selected System of Governments in the input$selectRegion_1 variable.This System of Government variable will be used in the title of the ggplot below.

```{r}
SystemsOfGovernment  <- eventReactive(c(input$selectSystemOfGovernment_1), { 
  library('stringr')
  str_c(input$selectSystemOfGovernment_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting system of government (notice - choices is set to the system of government variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectSystemOfGovernment_1", label = "Select System of Government",choices = systemsOfGovernment , multiple=TRUE, selected=c("Absolute_monarchy", "Republic", "Constitutional_monarchy", "n/a"))
)
```

#Render and Display Plots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

A question we had going into the data is what are the advnatages of spending money on healthare?
Measured as a percent of GDP spend on healthcare, what common health metrics improve with additional spending,
and is a certain system of government best for seeing improvement?

Spending % vs life expectancy - clear posititive trend for all three givernment types,
unsurprising

spending % vs contraceptive prevalance - doesnt seem to make a difference for
conctriutional monarchies, so what does cause contraceptive prevelance to change
in monarchys?

by plotting income vs contraceptive prevelance we can see a strong correlation bwteeen the two for monarchies,
indicating that the money the inidividual has matters more for contraceptives
(except for japan which is an outlier.......which is because
japan had a staggeringly high income per person due to the increase
in manufacturing and innovtation and patents or something)

the monarchys had a higher R^2 value for income vs contraceptive then the other government types
indicating that in monarchys the inidivudla income matters more

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Life Expectancy vs Health Expenditures", tabName = "scatter0", icon = icon("dashboard")),
      
      menuItem("Contraceptive Prevalence vs Health Expenditures", tabName = "scatter", icon = icon("dashboard")), 
      
      menuItem("Contraceptive Prevalence vs Income per Person", tabName = "scatter2", icon = icon("dashboard"))
      
    )
  ),
  dashboardBody(
    tabItems(
      # 0. "Life Expectancy vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter0",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("brandonsScatterPlot0UI.R",local = TRUE)$value
      ),
        
        
      # 1. "Contraceptive Prevalence vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html "),
        source("brandonsScatterPlot1UI.R",local = TRUE)$value
      ),
      
      # 2. "Contraceptive Prevalence vs Income per Person Scatter Plot" tab content
      tabItem(tabName = "scatter2",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html "),
        source("brandonsScatterPlot2UI.R",local = TRUE)$value
      )
      
    )
  )
)

source("brandonsScatterPlot0Server.R", local = TRUE)
source("brandonsScatterPlot1Server.R", local = TRUE)
source("brandonsScatterPlot2Server.R", local = TRUE)
```



Jeff's part from the "preapred for integration" version



```{r}
source("jeffDataA.R", local = TRUE)
source("jeffDataB.R", local = TRUE)

```


```{r}
projectJeff <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from WHO_Cleanest
 "), 
dataset = projectJeff)
```
#Plot Input

```{r}
inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("LATIN AMER. & CARIB",
"WESTERN EUROPE",
"ASIA (EX. NEAR EAST)",
"SUB-SAHARAN AFRICA",
"NORTHERN AMERICA",
"NEAR EAST",
"NORTHERN AFRICA",
"EASTERN EUROPE")),

  sliderInput("ContraFilter", label = "Average Contraceptive Prevalence:",
              min = 0, max = 100, value = c(0, 100), step = 10),
sliderInput("AgeFilter", label = "Average Median Age:",
              min = 0, max = 80, value = c(0, 80), step = 10)
)
```


#Render and Display Plots

The first bar chart shows the average contraceptive prevalence by both region (x-axis) and system of government (color). For two out of three regions which contain absolute monarchies, absolute monarchies perform poorly (low contraceptive prevalence) relative to other systems of government. For Western Europe, however, we see that absolute monarchies are the best performing system of government. To explore why this may be the case, we can observe the second bar chart. This bar chart shows the average population median age by region (x-axis) and system of government (color). It can be observed from this plot that out of those three regions with absolute monarchies, Western Europes countries with absolute monarchies have the highest average population median age. The higher median age of these countries could explain the higher access to contraceptives, as older people tend to be wiser and therefore likely familiar with the avenues of obtaining contraceptives.

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Contraceptive Bar Chart", tabName = "barchartJeff", icon = icon("dashboard")),
      menuItem("Age Bar Chart", tabName = "barchart2Jeff", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "BarChart2"
      tabItem(tabName = "barchartJeff",
        p("This is a barchart of Region and Contraceptive Prevalence"),
        source("jeffbarChart1UI.R",local = TRUE)$value
      ),
       # 2. "BarChart1"
      tabItem(tabName = "barchart2Jeff",
        p("This is a barchart of Region and Median Age"),
        source("jeffbarChart2UI.R",local = TRUE)$value
      )
    )
  )
)
source("jeffbarChart1Server.R", local = TRUE)
source("jeffbarChart2Server.R", local = TRUE)

```



dereks stuff


#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("derekDataA.R", local = TRUE)
source("derekDataB.R", local = TRUE)
source("derekDataC.R", local = TRUE)
```


#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
places <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
areas <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Regions <- eventReactive(c(input$selectRegion_1derek), { 
  library('stringr')
  str_c(input$selectRegion_1derek, collapse=', ')
})
```

```{r}
Reg <- eventReactive(c(input$selectReg_1), { 
  library('stringr')
  str_c(input$selectReg_1, collapse=', ')
})
```

```{r}
Re <- eventReactive(c(input$selectRegi_1), { 
  library('stringr')
  str_c(input$selectRegi_1, collapse=', ')
})
```





#Population Proportion, Age Dependency Ratio, and Gross National Income per Capita

According to The Fund for Peace and Foreign Policy, population proportion under 15 years of age is a measure that can serve as an indication of a failed state. In looking at World Health Organization data across world regions, it can be observed that Sub-Saharan African countries constitute a notably large portion of those countries with over 25% of their  population under 15 years of age. This can be seen in the “Population Proportion Under 15 years of Age” Histogram below.  In exploring how population proportion under 15 years of age affects the average country in a region, two measures, Age Dependency Ratio and Gross National Income per Capita, were examined.

Age Dependency Ratio (DR) is an indicator calculated by summing the population under 15 years of age with the population over 65 years of age, and then dividing this sum by the population between ages 15 and 64 (the “productive” age group). DR essentially communicates the number of dependents that each “productive” member of society must provide for. It has many implications for the performance of national economies. The “Age Dependency Ratio” Bar Chart below shows that on average Sub-Saharan African countries have very high DR ratios. Sub-Saharan African countries displayed an average DR ratio of 0.89, much higher than the next highest ratio of 0.62, held by Western European countries (much more economically developed). The fact that a region so underdeveloped has such a relatively small amount of their population contributing to their national economy does not portend well for them. In short, a high DR ratio means that a small portion of a country’s population is contributing to economic output, and bolstering many dependents. How far could this output be going? This idea was further explored through Gross National Income per Capita. 

Gross National Income per Capita is a country’s total income in a year divided by its population. It measures the average income of citizens in a country. The results for Gross National Income per Capita were not surprising for Sub-Saharan African Countries on average. The “Gross National Income per Capita” Boxplot below shows that Sub-Saharan African Countries had the lowest average incomes, with the lowest minimum, first quartile, median, third quartile, and maximum average incomes. This observation goes hand in hand with their low DR ratio, and thus isn’t profound. Obviously, with such a small portion of their population producing economically, the national aggregate income is being allocated over an excess of unproductive citizens, thus yielding a low Gross National Income per Capita. 

Surprisingly (and maybe counterintuitively), although Western European countries recorded the second highest DR ratio, they also had the second highest Gross National Income per Capita. This is striking as it would be expected that they suffer the difficulties of having such a large portion of unproductive citizens. The key to this is in realizing that Western European countries are amongst the most technologically, economically, and socially advanced, especially under western criteria. Because of this, the relatively small portion of productive people in the region can produce economic output that surpasses that from other regions. The same cannot be said for the still developing Sub-Saharan African countries. 


```{r}
inputPanel(
  selectInput("selectRegion_1derek", label = "Select Region for Population Proportion Under 15 years",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
  sliderInput("PopFilter_1", label = "Population Proportion Under 15:", min = 0, max = 100, value = c(0, 100), step = 1),
  selectInput("selectRegi_1", label = "Select Region for Age Dependency Ratio",choices = places, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA"))
)
```

```{r}
inputPanel(
  selectInput("selectReg_1", label = "Select Region for Gross National Income",choices = areas, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("incomeFilter_1", label = "Gross National Income Per Capita:", min = 0, max = 60870, value = c(0, 60870), step = 100)
)
```




#Render and Display the BoxPlots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Population Proportion Under 15 years Histogram", tabName = "Histo1", icon = icon("dashboard")),
      menuItem("Age Dependency Ratio Barchart", tabName = "barchart1", icon = icon("dashboard")),
      menuItem("Gross National Income per Capita Boxplot", tabName = "boxplot", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Population Proportion Under 15 years Histogram" tab content
      tabItem(tabName = "Histo1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("derekBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Dependent Ratio Barchart" tab content
      tabItem(tabName = "barchart1",
        p("And here."),
        source("derekbarChart2UI.R",local = TRUE)$value
        ),
      # 3. "Gross National Income per Capita Boxplot" tab content
      tabItem(tabName = "boxplot",
        p("And here."),
        source("derekBoxPlot2UI.R",local = TRUE)$value
        )
      )
    )
  )


source("derekBoxPlot1Server.R", local = TRUE)
source("derekbarChart2Server.R", local = TRUE)
source("derekBoxPlot2Server.R", local = TRUE)
```