---
title: "Brandon's Scatterplots"
author: "Brandon Kerbow"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, Brandon's portion of project 3. 

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(leaflet)
knitr::opts_chunk$set(echo = TRUE)
```

#Tableau Link

#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("DataA.R", local = TRUE)
```

#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
systemsOfGovernment <- data.world::query(data.world::qry_sql(
 "   
	select distinct system_of_government from who_cleanest

 "), 
dataset = project)
```

#Create a System of Government Variable
Create a System of Government variable with a string constructed from the selected System of Governments in the input$selectRegion_1 variable.This System of Government variable will be used in the title of the ggplot below.

```{r}
SystemsOfGovernment  <- eventReactive(c(input$selectSystemOfGovernment_1), { 
  library('stringr')
  str_c(input$selectSystemOfGovernment_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting system of government (notice - choices is set to the system of government variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectSystemOfGovernment_1", label = "Select Region",choices = systemsOfGovernment , multiple=TRUE, selected=c("Absolute_monarchy", "Republic", "Constitutional_monarchy", "n/a"))
)
```

#Render and Display Plots

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("menuItem - Contraceptive Prevalence vs Health Expenditures (% of GDP) Scatter Plot", tabName = "scatter", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Contraceptive Prevalence vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("ScatterPlot1UI.R",local = TRUE)$value
      )
    )
  )
)
source("ScatterPlot1Server.R", local = TRUE)
```


