---
title: "Top Hat Histograms"
author: "Dr. Cannata"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```



```{r}
source("jeffDataA.R", local = TRUE)
source("jeffDataB.R", local = TRUE)

```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from WHO_Cleanest
 "), 
dataset = project)
```
#Plot Input

```{r}
inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("LATIN AMER. & CARIB",
"WESTERN EUROPE",
"ASIA (EX. NEAR EAST)",
"SUB-SAHARAN AFRICA",
"NORTHERN AMERICA",
"NEAR EAST",
"NORTHERN AFRICA",
"EASTERN EUROPE")),
  sliderInput("ContraFilter", label = "Average Contraceptive Prevalence:",
              min = 0, max = 180, value = c(0, 180), step = 10)
)
```
**Only first 10 countries will be shown**

#Render and Display Plots

The first bar chart shows the average contraceptive prevalence by both region (x-axis) and system of government (color). For two out of three regions which contain absolute monarchies, absolute monarchies perform poorly (low contraceptive prevalence) relative to other systems of government. For Western Europe, however, we see that absolute monarchies are the best performing system of government. To explore why this may be the case, we can observe the second bar chart. This bar chart shows the average population median age by region (x-axis) and system of government (color). It can be observed from this plot that out of those three regions with absolute monarchies, Western Europe’s countries with absolute monarchies have the highest average population median age. The higher median age of these countries could explain the higher access to contraceptives, as older people tend to be wiser and therefore likely familiar with the avenues of obtaining contraceptives.

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Contraceptive Bar Chart", tabName = "barchart", icon = icon("dashboard")),
      menuItem("Age Bar Chart", tabName = "barchart2", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "BarChart2"
      tabItem(tabName = "barchart",
        p("This is a barchart of Region and Contraceptive Prevalence"),
        source("jeffbarChart1UI.R",local = TRUE)$value
      ),
       # 2. "BarChart1"
      tabItem(tabName = "barchart2",
        p("This is a barchart of Region and Median Age"),
        source("jeffbarChart2UI.R",local = TRUE)$value
      )
    )
  )
)
source("jeffbarChart1Server.R", local = TRUE)
source("jeffbarChart2Server.R", local = TRUE)

```
