---
title: "Top Hat Histograms"
author: "Dr. Cannata"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```

#Section for Links
data.world Project link.

GitHub Classroom Repository link.

#Create Dataframes
The sourced code below contains Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code and queries for the SuperStore database at data.world. The data is saved in variables as functions that return an R dataframe. These are examples data.world parameterized queries; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}
source("JeffData.R", local = TRUE)

```

#Retrieve Regions from the SuperStore dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-2" 
data.world::set_config(cfg_env("DW_API")) 
cities <- data.world::query(data.world::qry_sql(
 "   
	select distinct provider_city
	from hospital_visit_data_tx 
 "), 
dataset = project)
```
#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Cities <- eventReactive(c(input$selectCity_1), { 
  library('stringr')
  str_c(input$selectCity_1, collapse=', ')
})
```

#Create Panel with Select List
The following code creates an input panel for the Interactive Document, which has a [select box](https://shiny.rstudio.com/reference/shiny/latest/selectInput.html) for selecting regions (notice - choices is set to the regions variable that was loaded by the previous query) For a complete list of Shiny functions, please see this [link](https://shiny.rstudio.com/reference/shiny/latest/).

```{r}
inputPanel(
  selectInput("selectCity_1", label = "Select Provider City",choices = cities, multiple=TRUE, selected=c("HOUSTON", "DALLAS", "AUSTIN", "SAN ANTONIO")),
  sliderInput("PaymentFilter", label = "Average Total Payment:",
              min = 2000, max = 91000, value = c(0, 100200), step = 1000)
)
```
**Only first 10 cities will be shown**

#Render and Display the Shipping Costs Histograms

Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Hospital Costs Histogram", tabName = "histogram", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Hospital Costs Histogram" tab content
      tabItem(tabName = "histogram",
        p("This is a histogram of average total payments with colors indicating different Texas cities"),
        source("Histogram1UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram1Server.R", local = TRUE)

```

#Essential steps to add a new plot:
##1. Copy and change "newplot" to "newnewplot"  
    ,
      menuItem("Sales Histogram", tabName = "newplot", icon = icon("dashboard"))  
###  To  
    ,
      menuItem("Sales Histogram", tabName = "newnewplot", icon = icon("dashboard"))  
##2. Copy and make changes in three places as indicated below  
    ,  
      # 4. "Sales Histogram" tab content  
      tabItem(tabName = "newplot",  
        p("And even here."),  
        source("NewPlot1UI.R",local = TRUE)$value  
      )  
###  To  
    ,  
      # 5. "Sales Histogram 2" tab content   <- Change  
      tabItem(tabName = "newnewplot",        <- Change  
        p("And even here."),  
        source("NewNewPlot1UI.R",local = TRUE)$value   <- Change  
      )  
##3. Copy and change "NewPlot1Server.R" to "NewNewPlot1Server.R"  
      source("NewPlot1Server.R", local = TRUE)  
###   To  
      source("NewNewPlot1Server.R", local = TRUE)   <- Change  
##4. Open a UI.R file, save as a new UI.R file, change __N_ to __M_ 

##5. Open a Server.R file, save as a new Server.R file, change __N_ to __M_  

# Make a Second Dashboard  
##1. Copy and Paste the Dashboards chunk above.  
##2. Remove all but on sidebarMenu item.
##3. Rename the source files to new source files as in Steps 2 and 3 above.
##4. Create the new UI.R and Server.R files as in Steps 4 and 5 above.
##5. Add more sidebarMenu items as outlined above.

#Appendix
Data Cleaning Code.


