---
title: "TX Hospital Region Boxplot"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
<iframe src="https://public.tableau.com/views/Project2_Insight_Total_Payment_vs_Medicare_Payment/payment_comparison_dashboard?:showVizHome=no"width="800" height="800"></iframe>

This is an R Interactive Document, which uses the [R Markdown](http://rmarkdown.rstudio.com/authoring_basics.html) language to generate HTML. For a brief introduction to R Markdown, please review this [video](https://www.youtube.com/watch?v=DNS7i2m4sB0&feature=youtu.be).

#Load Packages
This [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) loads the packages required to run the R code in the document.
The last line of this code chunk enables document caching, which is expalined at this [link](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).

```{r setup, echo=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

#Display Session Information
The [sessionInfo() fuction](https://cran.r-project.org/web/packages/sessioninfo/sessioninfo.pdf) queries and prints information about the current R session including  information about packages, and from where they were installed.
```{r}
sessionInfo()
```



#Retrieve data from the  dataset
The following query retrieves the distinct region names from the SuperStore dataset at data.world and saves the region names in the regions variable.
```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
hospital_regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct hospital_visit_data_tx.hospital_referral_region_description from hospital_visit_data_tx
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-2" 
data.world::set_config(cfg_env("DW_API")) 
cities <- data.world::query(data.world::qry_sql(
 "   
	select distinct provider_city
	from hospital_visit_data_tx 
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
diseases <- data.world::query(data.world::qry_sql(
 "   
	select distinct hospital_visit_data_tx.drg_definition from hospital_visit_data_tx
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
drg <- data.world::query(data.world::qry_sql(
 "   
	select distinct drg_definition from hospital_visit_data_tx
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
medpayments <- data.world::query(data.world::qry_sql(
 "   
	select distinct average_medicare_payments from hospital_visit_data_tx
 "), 
dataset = project)
```
#Create Dataframe with region, category, sales, and order_date data
The following Shiny [eventReactive](https://shiny.rstudio.com/reference/shiny/1.0.1/observeEvent.html) code runs a query that retrieves the region, category, and sales data from the SuperStore database at data.world and saves it in the df variable as a function that returns an R dataframe. This is an example of a data.world parameterized query; details for data.world queries can be found at this [link](https://cran.r-project.org/web/packages/data.world/vignettes/query.html). The "?"s in the query are parameters. The parameters are filled in (in order) by the paramQuery$params statement.

```{r}

df <- eventReactive(c(input$selectHospital_Region_1, input$average_total_payments_filter_1), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select hospital_referral_region_description, drg_definition, average_total_payments
  	from hospital_visit_data_tx h
    where average_total_payments between ? and ? and hospital_referral_region_description in (?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?) and drg_definition in ('HEART FAILURE & SHOCK W/O CC/MCC', 'OTHER VASCULAR PROCEDURES W MCC', 'HEART FAILURE & SHOCK W MCC', 'SIMPLE PNEUMONIA & PLEURISY W MCC', 'RENAL FAILURE W MCC', 'SIMPLE PNEUMONIA & PLEURISY W CC', 'OTHER VASCULAR PROCEDURES W CC', 'HEART FAILURE & SHOCK W CC', 'G.I. HEMORRHAGE W MCC', 'CELLULITIS W/O MCC')

order by hospital_referral_region_description
   ")
  paramQuery$params <- c(input$average_total_payments_filter_1[1], input$average_total_payments_filter_1[2], input$selectHospital_Region_1[1], input$selectHospital_Region_1[2], input$selectHospital_Region_1[3], input$selectHospital_Region_1[4], input$selectHospital_Region_1[5], input$selectHospital_Region_1[6], input$selectHospital_Region_1[7], input$selectHospital_Region_1[8], input$selectHospital_Region_1[9], input$selectHospital_Region_1[10], input$selectHospital_Region_1[11], input$selectHospital_Region_1[12], input$selectHospital_Region_1[13], input$selectHospital_Region_1[14], input$selectHospital_Region_1[15], input$selectHospital_Region_1[16], input$selectHospital_Region_1[17], input$selectHospital_Region_1[18], input$selectHospital_Region_1[19], input$selectHospital_Region_1[20], input$selectHospital_Region_1[21], input$selectHospital_Region_1[22], input$selectHospital_Region_1[23], input$selectHospital_Region_1[24])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
df1 <- eventReactive(c(input$selectHospital_Region_1, input$yDataMin__1_, input$yDataMax__1_, input$average_total_payments_filter_1), { 
  if( ! is.na(input$yDataMin__1_) & ! is.na(input$yDataMax__1_)) {
    df() %>% dplyr::filter(between(average_total_payments, input$yDataMin__1_, input$yDataMax__1_))
  }
  else {
    df()
  }
})
```


```{r}

df2 <- eventReactive(c(input$selectdrg_definition_3, input$average_total_payments_filter_3), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select hospital_referral_region_description, drg_definition, average_total_payments
  	from hospital_visit_data_tx h
    where average_total_payments between ? and ? and drg_definition in (?, ?, ?, ?, ?, ?, ?, ?, ?, ?) and  hospital_referral_region_description  in 

('TX - Houston', 'TX - Dallas', 'TX - Fort Worth', 'TX - San Antonio', 'TX - Austin', 'TX - McAllen', 'TX - Harlingen', 'TX - El Paso', 'TX - Tyler', 'TX - Lubbock') 


order by drg_definition
   ")
  paramQuery$params <- c(input$average_total_payments_filter_3[1], input$average_total_payments_filter_3[2], input$selectdrg_definition_3[1], input$selectdrg_definition_3[2], input$selectdrg_definition_3[3], input$selectdrg_definition_3[4], input$selectdrg_definition_3[5], input$selectdrg_definition_3[6], input$selectdrg_definition_3[7], input$selectdrg_definition_3[8], input$selectdrg_definition_3[9], input$selectdrg_definition_3[10])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
df3 <- eventReactive(c(input$selectdrg_definition_3, input$yDataMin__3_, input$yDataMax__3_,input$average_total_payments_filter_3), { 
  if( ! is.na(input$yDataMin__3_) & ! is.na(input$yDataMax__3_)) {
    df2() %>% dplyr::filter(between(average_total_payments, input$yDataMin__3_, input$yDataMax__3_))
  }
  else {
    df2()
  }
})
```

```{r}

df4 <- eventReactive(c(input$selectdrg_definition_1, input$average_medicare_payments_filter_1), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select drg_definition, average_medicare_payments
  	from hospital_visit_data_tx h
    where average_medicare_payments between ? and ? and drg_definition in ('ESOPHAGITIS, GASTROENT & MISC DIGEST DISORDERS W/O MCC', 'HEART FAILURE & SHOCK W CC', 'KIDNEY & URINARY TRACT INFECTIONS W/O MCC', 'MISC DISORDERS OF NUTRITION,METABOLISM,FLUIDS/ELECTROLYTES W/O MCC', 'SIMPLE PNEUMONIA & PLEURISY W CC')

order by drg_definition
   ")
  paramQuery$params <- c(input$average_medicare_payments_filter_1[1], input$average_medicare_payments_filter_1[2])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
df5 <- eventReactive(c(input$selectdrg_definition_1, input$yDataMin__1_, input$yDataMax__1_, input$average_medicare_payments_filter_1), { 
  if( ! is.na(input$yDataMin__1_) & ! is.na(input$yDataMax__1_)) {
    df4() %>% dplyr::filter(between(average_medicare_payments, input$yDataMin__1_, input$yDataMax__1_))
  }
  else {
    df4()
  }
})
```

#Create a Regions Variable
Create a Regions variable with a string constructed from the selected regions in the input$selectRegion_1 variable.This Regions variable will be used in the title of the ggplot below.

```{r}
Hospital_Regions <- eventReactive(c(input$selectHospital_Region_1), { 
  library('stringr')
  str_c(input$selectHospital_Region_1, collapse=', ')
})
```

```{r}
Diseases <- eventReactive(c(input$selectdrg_definition_3), { 
  library('stringr')
  str_c(input$selectdrg_definition_3, collapse=', ')
})
```

```{r}
Drgs <- eventReactive(c(input$selectdrg_definition_1), { 
  library('stringr')
  str_c(input$selectdrg_definition_1, collapse=', ')
})
```


#Brandon's Boxplot

```{r}
inputPanel(
  selectInput("selectHospital_Region_1", label = "Select Hospital Region",choices = hospital_regions, multiple=TRUE, selected=c("AR - Texarkana", "LA - Shreveport", "TX - Abilene", "TX - Amarillo", "TX - Austin", "TX - Beaumont", "TX - Bryan", "TX - Corpus Christi", "TX - Dallas", "TX - El Paso", "TX - Fort Worth", "TX - Harlingen", "TX - Houston", "TX - Longview", "TX - Lubbock", "TX - McAllen", "TX - Odessa", "TX - San Angelo", "TX - San Antonio", "TX - Temple", "TX - Tyler", "TX - Victoria", "TX - Waco", "TX - Wichita Falls")
              )
  ,sliderInput("average_total_payments_filter_1", label = "Average Total Payments:", min = 0, max = 91000, value = c(0, 91000), step = 100)
)
```



Using [ggplotly](https://www.rdocumentation.org/packages/plotly/versions/4.7.1/topics/ggplotly) and [shinydashborad](https://rstudio.github.io/shinydashboard/structure.html#dynamic-content-1)

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Total Payment vs Disease", tabName = "boxplot1", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Total Payment vs Diseaset" tab content
      tabItem(tabName = "boxplot1",
        source("BoxPlot1UI.R",local = TRUE)$value
      )
    )
  )
)
source("BoxPlot1Server.R", local = TRUE)
```
 

#Kyle's Boxplot
```{r}
inputPanel(
  selectInput
  ("selectdrg_definition_3", label = "Select dieases",choices = diseases, multiple=TRUE, selected=c("HEART FAILURE & SHOCK W/O CC/MCC", "OTHER VASCULAR PROCEDURES W MCC", "HEART FAILURE & SHOCK W MCC", "SIMPLE PNEUMONIA & PLEURISY W MCC", "RENAL FAILURE W MCC", "SIMPLE PNEUMONIA & PLEURISY W CC", "OTHER VASCULAR PROCEDURES W CC", "HEART FAILURE & SHOCK W CC", "G.I. HEMORRHAGE W MCC", "CELLULITIS W/O MCC")
    
  )
  
  ,sliderInput("average_total_payments_filter_3", label = "Average Total Payments:", min = 0, max = 50000, value = c(0, 50000), step = 100)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Total Payment vs Disease", tabName = "boxplot3", icon = icon("dashboard3"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Total Payment vs Diseases" tab content
      tabItem(tabName = "boxplot3",
        source("BoxPlot3UI.R",local = TRUE)$value
      )
    )
  )
)
source("BoxPlot3Server.R", local = TRUE)
```
  

#Jeffrey's Histogram
```{r}
source("JeffData.R", local = TRUE)

```

```{r}
inputPanel(
  selectInput("selectCity_1", label = "Select Provider City",choices = cities, multiple=TRUE, selected=c("HOUSTON", "DALLAS", "AUSTIN", "SAN ANTONIO")),
  sliderInput("PaymentFilter", label = "Average Total Payment:",
              min = 2000, max = 91000, value = c(0, 100200), step = 1000)
)
```
**Only first 10 cities will be shown**

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Hospital Costs Histogram", tabName = "histogram", icon = icon("dashboard2"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Hospital Costs Histogram" tab content
      tabItem(tabName = "histogram",
        p("This is a histogram of average total payments with colors indicating different Texas cities"),
        source("Histogram1UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram1Server.R", local = TRUE)

```
# Derek's Plots 
```{r}
inputPanel(
  selectInput("selectdrg_definition_1", label = "Select DRG Definition",choices = drg, multiple=TRUE, selected=c('ESOPHAGITIS, GASTROENT & MISC DIGEST DISORDERS W/O MCC', 'HEART FAILURE & SHOCK W CC', 'KIDNEY & URINARY TRACT INFECTIONS W/O MCC', 'MISC DISORDERS OF NUTRITION,METABOLISM,FLUIDS/ELECTROLYTES W/O MCC', 'SIMPLE PNEUMONIA & PLEURISY W CC')
              )
  ,sliderInput("average_medicare_payments_filter_1", label = "Average Medicare Payments:", min = 0, max = 91000, value = c(0, 91000), step = 100)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Medicare Payments marked by Disease", tabName = "histo2", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Medicare Payment marked by Disease" tab content
      tabItem(tabName = "histo2",
        source("MedHistoUI.R",local = TRUE)$value
      )
    )
  )
)
source("MedHistoServer.R", local = TRUE)
