---
title: "TX Hospital Region Boxplot"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---


#Dataset Description

The dataset visualized in this interactive document shows data over Texas Hospitals in 2017. Specifically, it shows - for a given hospital and a given DRG Definition (diagnosis) - metrics such as the average price and average amount covered by medicare. 

#Important Links

[Data.world Project](https://data.world/jeffrey-feng/s18-edv-project-2)

Kyle's Insights: [1](https://data.world/jeffrey-feng/s18-edv-project-2/insights/479959a2-7cf4-4112-8bf7-604b06fde898)
[2](https://data.world/jeffrey-feng/s18-edv-project-2/insights/b18d3ebf-d075-4e77-9750-70a3198fa4c3)

Jeffrey's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-2/insights/24cd17df-fa5e-4c76-969c-4b4f9a68d832)
[2](https://data.world/jeffrey-feng/s18-edv-project-2/insights/2032ebd3-69b2-4386-8681-2aa1fbe244ae)

Brandon's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-2/insights/3d7bd211-95c2-4169-a3dd-5bd62b826171)
[2](https://data.world/jeffrey-feng/s18-edv-project-2/insights/32b72878-8102-49ae-a176-06abef591179)
[3](https://data.world/jeffrey-feng/s18-edv-project-2/insights/5730154c-877a-4e6b-b8f2-e99176f59935)

Derek's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-2/insights/c290f85e-4dc7-44ca-b63c-1160205ba86a)
[2](https://data.world/jeffrey-feng/s18-edv-project-2/insights/03464bb2-0a41-4caa-afb2-7d6f826d3445)

[Github Repository](https://github.com/CannataUTDV/s18dvproject1-duquesnay-feng-kerbow-orji)


#Embedded Tableau Insight

(Note: this this embedded Tableau Insight only appears if this document is being viewed in browser).
These dual-axis visuals show the comparison of the average total payment vs the average medicare payment to Texas hospitals in 2017. The data is grouped by diagnosis and the user can filter by hospital region.

In all cases, the total payment will at or above the total Medicare payment because up to 100% of bills can be covered by Medicare. Only the top 5 diagnoses are listed, determined by total revenue across all hospitals.

The top and bottom visuals can be independently filtered for any given set of hospital regions. The default rendering shows the top visual including all regions, and the bottom visual including only the Harlingen, TX. 
For this rendering, it can be observed that the hospitals in the Harlingen region have a disproportionally high amount of medical bills covered by Medicare compared to the average of all regions. The reason for this is a 
subject of further investigation but one possible explanation could be level of income.

<iframe src="https://public.tableau.com/views/Project2_Insight_Total_Payment_vs_Medicare_Payment/payment_comparison_dashboard?:showVizHome=no"width="800" height="800"></iframe>



```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
hospital_regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct hospital_visit_data_tx.hospital_referral_region_description from hospital_visit_data_tx
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-2" 
data.world::set_config(cfg_env("DW_API")) 
cities <- data.world::query(data.world::qry_sql(
 "   
	select distinct provider_city
	from hospital_visit_data_tx 
 "), 
dataset = project)
```

```{r}
project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
data.world::set_config(cfg_env("DW_API")) 
diseases <- data.world::query(data.world::qry_sql(
 "   
	select distinct hospital_visit_data_tx.drg_definition from hospital_visit_data_tx
 "), 
dataset = project)
```



```{r}

df <- eventReactive(c(input$selectHospital_Region_1, input$average_total_payments_filter_1), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select hospital_referral_region_description, drg_definition, average_total_payments
  	from hospital_visit_data_tx h
    where average_total_payments between ? and ? and hospital_referral_region_description in (?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?, ?) and drg_definition in ('HEART FAILURE & SHOCK W/O CC/MCC', 'OTHER VASCULAR PROCEDURES W MCC', 'HEART FAILURE & SHOCK W MCC', 'SIMPLE PNEUMONIA & PLEURISY W MCC', 'RENAL FAILURE W MCC', 'SIMPLE PNEUMONIA & PLEURISY W CC', 'OTHER VASCULAR PROCEDURES W CC', 'HEART FAILURE & SHOCK W CC', 'G.I. HEMORRHAGE W MCC', 'CELLULITIS W/O MCC')

order by hospital_referral_region_description
   ")
  paramQuery$params <- c(input$average_total_payments_filter_1[1], input$average_total_payments_filter_1[2], input$selectHospital_Region_1[1], input$selectHospital_Region_1[2], input$selectHospital_Region_1[3], input$selectHospital_Region_1[4], input$selectHospital_Region_1[5], input$selectHospital_Region_1[6], input$selectHospital_Region_1[7], input$selectHospital_Region_1[8], input$selectHospital_Region_1[9], input$selectHospital_Region_1[10], input$selectHospital_Region_1[11], input$selectHospital_Region_1[12], input$selectHospital_Region_1[13], input$selectHospital_Region_1[14], input$selectHospital_Region_1[15], input$selectHospital_Region_1[16], input$selectHospital_Region_1[17], input$selectHospital_Region_1[18], input$selectHospital_Region_1[19], input$selectHospital_Region_1[20], input$selectHospital_Region_1[21], input$selectHospital_Region_1[22], input$selectHospital_Region_1[23], input$selectHospital_Region_1[24])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
df1 <- eventReactive(c(input$selectHospital_Region_1, input$yDataMin__1_, input$yDataMax__1_, input$average_total_payments_filter_1), { 
  if( ! is.na(input$yDataMin__1_) & ! is.na(input$yDataMax__1_)) {
    df() %>% dplyr::filter(between(average_total_payments, input$yDataMin__1_, input$yDataMax__1_))
  }
  else {
    df()
  }
})
```


```{r}

df2 <- eventReactive(c(input$selectdrg_definition_3, input$average_total_payments_filter_3), { 
  project <- "https://data.world/brandon-kerbow/s18-edv-project-2-dataset" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
   "   
  	select hospital_referral_region_description, drg_definition, average_total_payments
  	from hospital_visit_data_tx h
    where average_total_payments between ? and ? and drg_definition in (?, ?, ?, ?, ?, ?, ?, ?, ?, ?) and  hospital_referral_region_description  in 

('TX - Houston', 'TX - Dallas', 'TX - Fort Worth', 'TX - San Antonio', 'TX - Austin', 'TX - McAllen', 'TX - Harlingen', 'TX - El Paso', 'TX - Tyler', 'TX - Lubbock') 


order by drg_definition
   ")
  paramQuery$params <- c(input$average_total_payments_filter_3[1], input$average_total_payments_filter_3[2], input$selectdrg_definition_3[1], input$selectdrg_definition_3[2], input$selectdrg_definition_3[3], input$selectdrg_definition_3[4], input$selectdrg_definition_3[5], input$selectdrg_definition_3[6], input$selectdrg_definition_3[7], input$selectdrg_definition_3[8], input$selectdrg_definition_3[9], input$selectdrg_definition_3[10])
  data.world::query(paramQuery, dataset = project)
}) 
```

```{r}
df3 <- eventReactive(c(input$selectdrg_definition_3, input$yDataMin__3_, input$yDataMax__3_,input$average_total_payments_filter_3), { 
  if( ! is.na(input$yDataMin__3_) & ! is.na(input$yDataMax__3_)) {
    df2() %>% dplyr::filter(between(average_total_payments, input$yDataMin__3_, input$yDataMax__3_))
  }
  else {
    df2()
  }
})
```


```{r}
Hospital_Regions <- eventReactive(c(input$selectHospital_Region_1), { 
  library('stringr')
  str_c(input$selectHospital_Region_1, collapse=', ')
})
```

```{r}
Diseases <- eventReactive(c(input$selectdrg_definition_3), { 
  library('stringr')
  str_c(input$selectdrg_definition_3, collapse=', ')
})
```

#Boxplot 1 - Average Total Payment vs Disease

This boxplot can be viewed by clicking the blue "Average Total Payment vs Disease" button next to the plot below. This visual shows the distribution of the Average Total Payments for the ten most common Diseases (DRG Definitions). Each color corresponds to a different hospital region. This allows the user to make comparisons across both disease and city. For example, when we plot Austin, Dallas, Houston, and Harlingen we can see that Harlingen is consistently more expensive than the major Texas cities. This could indicate a shortage of doctors/specialists in the area.

```{r}
inputPanel(
  selectInput("selectHospital_Region_1", label = "Select Hospital Region",choices = hospital_regions, multiple=TRUE, selected=c("AR - Texarkana", "LA - Shreveport", "TX - Abilene", "TX - Amarillo", "TX - Austin", "TX - Beaumont", "TX - Bryan", "TX - Corpus Christi", "TX - Dallas", "TX - El Paso", "TX - Fort Worth", "TX - Harlingen", "TX - Houston", "TX - Longview", "TX - Lubbock", "TX - McAllen", "TX - Odessa", "TX - San Angelo", "TX - San Antonio", "TX - Temple", "TX - Tyler", "TX - Victoria", "TX - Waco", "TX - Wichita Falls")
              )
  ,sliderInput("average_total_payments_filter_1", label = "Average Total Payments:", min = 0, max = 50000, value = c(0, 50000), step = 100)
)
```


```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Total Payment vs Disease", tabName = "boxplot1", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Total Payment vs Diseaset" tab content
      tabItem(tabName = "boxplot1",
        source("BoxPlot1UI.R",local = TRUE)$value
      )
    )
  )
)
source("BoxPlot1Server.R", local = TRUE)
```
 

#Boxplot 2 - Average Total Payment vs Region

This boxplot can be viewed by clicking the blue "Average Total Payment vs Region" button next to the plot below. This visual shows the distribution of the average total payments for the ten regions which generate the most revenue. Each color corresponds to a different DRG Definition, allowing the user to make comparisons across both city and disease. For example, when we plot vascular problems, heart failures and renal failures across the regions we see that vascular problems incur the highest payments in the Houston and Dallas region, which could imply either a higher quality of service or a shortage of cardiovascular doctors in the region. 

```{r}
inputPanel(
  selectInput
  ("selectdrg_definition_3", label = "Select dieases",choices = diseases, multiple=TRUE, selected=c("HEART FAILURE & SHOCK W/O CC/MCC", "OTHER VASCULAR PROCEDURES W MCC", "HEART FAILURE & SHOCK W MCC", "SIMPLE PNEUMONIA & PLEURISY W MCC", "RENAL FAILURE W MCC", "SIMPLE PNEUMONIA & PLEURISY W CC", "OTHER VASCULAR PROCEDURES W CC", "HEART FAILURE & SHOCK W CC", "G.I. HEMORRHAGE W MCC", "CELLULITIS W/O MCC")
    
  )
  
  ,sliderInput("average_total_payments_filter_3", label = "Average Total Payments:", min = 0, max = 50000, value = c(0, 50000), step = 100)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Average Total Payment vs Region", tabName = "boxplot3", icon = icon("dashboard3"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Total Payment vs Region" tab content
      tabItem(tabName = "boxplot3",
        source("BoxPlot3UI.R",local = TRUE)$value
      )
    )
  )
)
source("BoxPlot3Server.R", local = TRUE)
```
  

#Histogram - Hospital Costs by City

This histogram + corresponding density plot can be viewed by clicking the blue "Hospital Cost Histogram" button next to the plot below. The density plot displays the average total payments and the cities are color coded. Up to the first 10 selected cities will be shown in order to keep the histogram legible. By default, the four largest cities in Texas are shown. As shown by the histogram, the lower costs are fairly spread out throughout the four cities. As the cost increases, however, cities such as Houston and Dallas start to be the large majority of the bin. This is especially clear if the user clicks the zoom tool and zooms in to the right side of the histogram or by using the slider for average total payment to reduce the range to the more expensive costs. Dallas and Houston being overrepresented in the high-cost bins indicates that these cities could have a lot of specialized doctors or expensive procedures to offer, but further research would be required to arrive at a more confident conclusion.

```{r}
source("JeffData.R", local = TRUE)

```

```{r}
inputPanel(
  selectInput("selectCity_1", label = "Select Provider City",choices = cities, multiple=TRUE, selected=c("HOUSTON", "DALLAS", "AUSTIN", "SAN ANTONIO")),
  sliderInput("PaymentFilter", label = "Average Total Payment:",
              min = 2000, max = 91000, value = c(0, 100200), step = 1000)
)
```
**Only first 10 cities will be shown**

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Hospital Costs Histogram", tabName = "histogram", icon = icon("dashboard2"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Hospital Costs Histogram" tab content
      tabItem(tabName = "histogram",
        p("This is a histogram of average total payments with colors indicating different Texas cities"),
        source("Histogram1UI.R",local = TRUE)$value
      )
    )
  )
)
source("Histogram1Server.R", local = TRUE)

```


#Appendix: Data Cleaning Code
(Click "code" to your right to see the code)
```{r, eval= FALSE}
library(tidyverse)
csvURL <- "https://query.data.world/s/5-OstD__RjYPgomgoP0k5_w6DBayoe"
df <- read_csv(csvURL, col_types = list(
  DRG_Definition = col_character(),
  Provider_Id = col_number(),
  Provider_Name = col_character(),
  Provider_Street_Address = col_character(),
  Provider_City = col_character(),
  Provider_State = col_character(),
  Provider_Zip_Code = col_number(),
  Hospital_Referral_Region_Description = col_character(),
  Total_Discharges = col_number(),
  Average_Covered_Charges = col_number(), #changed to numbers
  Average_Total_Payments = col_number(), #changed to numbers
  Average_Medicare_Payments = col_number() #changed to numbers
))

names(df) <- gsub("[^ -~]", "", names(df)) 
names(df) <- gsub(" ", "_", names(df)) 

df$Average_Covered_Charges <- gsub("\\$", "", df$Average_Covered_Charges)
df$Average_Total_Payments <- gsub("\\$", "", df$Average_Total_Payments)
df$Average_Medicare_Payments <- gsub("\\$", "", df$Average_Medicare_Payments)


df$DRG_Definition <- gsub("[0123456789-]", "", df$DRG_Definition)
df$DRG_Definition <- gsub("  ", "", df$DRG_Definition)

df <- df %>% dplyr::mutate_all(funs(gsub(pattern="[^ -~]", replacement= "", .)))

write_csv(df, "C:/Users/bwkerbow/Desktop/Hospital_Visit_Data_TX.csv") 

df <- read_csv("C:/Users/bwkerbow/Desktop/Hospital_Visit_Data_TX.csv", col_types = list(
  DRG_Definition = col_character(),
  Provider_Id = col_number(),
  Provider_Name = col_character(),
  Provider_Street_Address = col_character(),
  Provider_City = col_character(),
  Provider_State = col_character(),
  Provider_Zip_Code = col_number(),
  Hospital_Referral_Region_Description = col_character(),
  Total_Discharges = col_number(),
  Average_Covered_Charges = col_number(), #changed to numbers
  Average_Total_Payments = col_number(), #changed to numbers
  Average_Medicare_Payments = col_number() #changed to numbers
))

write_csv(df, "C:/Users/bwkerbow/Desktop/Hospital_Visit_Data_TX.csv")
```