---
title: "WHO Data"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---
  

  
  
  
```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
data.world::set_config(cfg_env("DW_API")) 
countries <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.country from WHO_Cleanest
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
data.world::set_config(cfg_env("DW_API")) 
proportion <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.population_proportion_under_15
  from WHO_Cleanest
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/"  
data.world::set_config(cfg_env("DW_API")) 
children <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.children_per_woman from WHO_Cleanest
  "), 
  dataset = project)
```



```{r}

df <- eventReactive(c(input$selectChildren_1, input$selectProportion_1), { 
  project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
    "   
    select country, children_per_woman, population_proportion_under_15
    from WHO_Cleanest h
    where children_per_woman between ? and ? and population_proportion_under_15 between ? and ? and country in ('China', 'India', 'United States of America', 'Indonesia', 'Brazil', 'Pakistan', 'Bangladesh', 'Nigeria', 'Russia', 'Japan')
    
    order by Country
    ")
  paramQuery$params <- c(input$selectChildren_1[1], input$selectChildren_1[2], input$selectProportions_1[1], input$selectProportions_1[2])
  data.world::query(paramQuery, dataset = project)
}) 
```








```{r}
Countries <- eventReactive(c(input$selectCountries_1), { 
  library('stringr')
  str_c(input$selectCountries_1, collapse=', ')
})
```

hello
```{r}
Proportions <- eventReactive(c(input$selectProportions_1), { 
  library('stringr')
  str_c(input$selectProportions_1, collapse=', ')
})
```


```


#Boxplot 1

```{r}
inputPanel(
  selectInput
  ("selectCountries_1", label = "Select Countries",choices = countries, multiple=TRUE, selected=c("China", "India", "Bangladesh", "Indonesia", "Russia", "Japan", "Brazil", "Nigeria", "United States of America", "Pakistan")
    
  )
  
  ,sliderInput("selectChildren_1", label = "Children per woman:", min = 0, max = 8, value = c(0, 8), step = .2)
  ,sliderInput("selectProportions_1", label = "Proportion of population under 15:", min = 0, max = 100, value = c(0, 100), step = 2)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("proportion of population under 15", tabName = "boxplot1", icon = icon("dashboard1"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Average Total Payment vs Region" tab content
      tabItem(tabName = "boxplot1",
              source("BoxPlot1UI.R",local = TRUE)$value
      )
    )
  )
)

source("BoxPlot1Server.R", local = TRUE)

```


