---
title: "The Health and Well-Being of Countries: An Interactive Document"
author: "Kyle DeQuesnay, Jeffrey Feng, Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

#Dataset Description
This dataset was obtained online from the World Health Organization (WHO) and contains various health-related metrics for every country on the planet. Examples of such metrics include the average per capita (per person) income and average life expectancy. 

To further segment the data we went to the UNESCO institute for statistics to join the fields of region (e.g. Western Europe, Sub-Saharan Africa) and the system of government in place (e.g. Republic, Absolute Monarchy) for each country. 

#Important Links

[Data.world Project](https://data.world/kyl617/s18-edv-final-project)



Kyle's Data.World Insights: 

[Quality of Life in relation to Contraceptive Prevalence](https://data.world/kyl617/s18-edv-final-project/insights/c2f01c89-67ac-4fa6-8232-17efc21d6d88)

[Exploration of Infant Mortality Rate](https://data.world/kyl617/s18-edv-final-project/insights/b77020d1-8ad4-4324-9c7b-31ba4bb794f3)


Jeffrey's Data.World Insights:

[HALE and Health Expenditure](https://data.world/kyl617/s18-edv-final-project/insights/5d555d5c-ea5f-477a-8e8b-75cfb0efb95e)

[Contraceptive Prevalence and Literacy Rate](https://data.world/kyl617/s18-edv-final-project/insights/dadd284a-8e76-4f3a-ba47-0bc4ca7f8997)

Brandon's Data.World Insights:

[Average Children per Women vs Average Annual Temperature by Country](https://data.world/kyl617/s18-edv-final-project/insights/248e546f-4b00-4536-a9ca-f41f7eafc061)

[Contraceptive Access and Median Age by Region and System of Government](https://data.world/kyl617/s18-edv-final-project/insights/eae60986-778f-488b-a29e-c55f5ebe7cbb)

[Number of Children per Women: By Geography and Infant Mortality Rate](https://data.world/kyl617/s18-edv-final-project/insights/440cd999-cba6-4cbe-8960-bd96694a12a9)

Derek's Data.World Insights:

[Frequncy of Population Proportion Under 15 and Effect on Gross National Income per Capita](https://data.world/kyl617/s18-edv-final-project/insights/a4460ccc-7b49-457a-b815-d034d8bbf673)

[Contraceptive Prevalence vs. Adult Literacy Rate](https://data.world/kyl617/s18-edv-final-project/insights/3560c82f-12b5-430d-823e-229678892446)




[Github Repository](https://github.com/CannataUTDV/s18dvfinalproject-duquesnay-feng-orji-kerbow)

#Summary of our Questions and Findings
*Does spending more money on healthcare increase the well-being of countries?
Not always the case, but usually other factors help explain what causes healthcare metrics to improve.

*What factors play into the availability of contraceptives?
Region, system of government, age, and education - but not always in the way we expected.

*Do countries which have a small portion of "working age" population tend to be more poor (per capita)?
This is actually not always the case.

*What factors play into the number of children per women and what accounts for the variability?
Although education is the strongest driver, the variability in this predictive model was not what we expected.

*Does System of Government tend to have an effect on quality of life, as measured through health metrics?
Yes, but which system of government tends to have the strongest metrics depends on the region



```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(leaflet)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

source("brandonsDataB.R", local = TRUE)
source("brandonsDataC.R", local = TRUE)
source("brandonsDataD.R", local = TRUE)

```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
systemsOfGovernment <- data.world::query(data.world::qry_sql(
 "   
	select distinct system_of_government from who_cleanest

 "), 
dataset = project)
```


```{r}
SystemsOfGovernment  <- eventReactive(c(input$selectSystemOfGovernment_1), { 
  library('stringr')
  str_c(input$selectSystemOfGovernment_1, collapse=', ')
})
```

#Dashboard 1 - Benefits of Spending on Healthcare
One important question surrounding the issue of global health is how much money countries should spend on improving it. To see what kind of returns countries can attain from spending, we focus on relationships between healthcare expenditure (% of GDP, with GDP being the total value of goods produced annually within a country) vs common health metrics such as life expectancy and contraceptive prevalence. We would expect that for any given system of government, an increase in spending tends to improve common health metrics, but we will observe that this is not the case.

##Tab 1 - Contraceptive Prevalence

*Contraceptive prevalence vs healthcare expenditure

*Countries as dots, trend lines by system of government

*Observation: for constitutional monarchies, there does not appear to be an increase in contraceptive prevalence that comes with an increasing in spending

*Why this may be the case is explored in the next tabs


##Tab 2 - Average Income per Capita

*Contraceptive prevalence vs income per capita

*Positive correlation for all systems of government, strongest R^2 value for constitutional monarchies

*Tabs 1 and 2 together indicate that for constitutional monarchies, contraceptive prevalence is not based on total healthcare expenditure of that country but rather the individual income 

*We explore residuals for the constitutional monarchies trend in the next visual

##Tab 3 - Average Residual by Region

*Analyzing the residuals of the "contraceptive prevalence vs income per capita" model for constitutional monarchies, i.e. the dark green line in the previous tab

*There is a clear pattern by region: African regions have less access to contraceptive prevalence than predicted by the model, Asia has more

*Summary of conclusion from tabs 1-3: In constitutional monarchies the arability of contraceptives depends on both individual income and region, whereas for other systems of government the total healthcare expenditure of the countries gives a stronger prediction.

```{r}
inputPanel(
  selectInput("selectSystemOfGovernment_1", label = "Select System of Government",choices = systemsOfGovernment , multiple=TRUE, selected=c("Absolute_monarchy", "Republic", "Constitutional_monarchy"))
)
```



```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(

      
      menuItem("Contraceptives vs Spending", tabName = "scatter", icon = icon("dashboard")), 
      
      menuItem("Contraceptives vs Income", tabName = "scatter2", icon = icon("dashboard")),
      
      menuItem("Average Residual by Region", tabName = "brandonboxplot1", icon = icon("dashboard"))
      
    )
  ),
  dashboardBody(
    tabItems(
 
        
        
      # 1. "Contraceptive Prevalence vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter",
        p("Absolute Monarchies (orange line) ~ P-value: 0.0026, R^2: 0.97..............................................        
           Republics (purple line) ~ P-value: 0.00013, R^2: 0.121 ..............................................................
            Constitutional Monarchies (dark green line) ~ P-value: 0.93, R^2: 0.0004.................................."),
        source("brandonsScatterPlot1UI.R",local = TRUE)$value
      ),
      
      # 2. "Contraceptive Prevalence vs Income per Person Scatter Plot" tab content
      tabItem(tabName = "scatter2",
        p("Absolute Monarchies (orange line) ~ P-value: 0.82, R^2: 0.074..............................................        
           Republics (purple line) ~ P-value: 0.0001, R^2: 0.204 ..............................................................
            Constitutional Monarchies (dark green line) ~ P-value: 0.012, R^2: 0.35.................................."),
        source("brandonsScatterPlot2UI.R",local = TRUE)$value
      ), 
      
      # 3. "Average residual by Region" tab content
      tabItem(tabName = "brandonboxplot1",
        p("Filter to show only Constitutional Monarchies"),
        source("brandonBarChart1UI.R",local = TRUE)$value
      )
      
    )
  )
)


source("brandonsScatterPlot1Server.R", local = TRUE)
source("brandonsScatterPlot2Server.R", local = TRUE)
source("brandonbarChart1Server.R", local = TRUE)

```


```{r}
source("jeffDataA.R", local = TRUE)
source("jeffDataB.R", local = TRUE)
source("jeffDataC.R", local = TRUE)

```


```{r}
project <- "https://data.world/kyl617/s18-edv-final-project" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from WHO_Cleanest2
 "), 
dataset = project)
```

#Dashboard 2 - Contraceptive Prevelance

A similar topic of interest is whether or not the system of government or region has a bearing on the contraceptive prevalence. Answers to this question are explored in the dashboard below. This dashboard contains three tabs with two bar charts and a scatter plot. The input panel controls the regions of the world which are shown and the top and bottom sliders control the range of y-values for the bar charts in the first and second tab, respectively. 

##Tab 1: By Region and Government
*Average contraceptive prevalence (y-axis) by both region (x-axis) and system of government (color)

*We thought Republics would have the best access to contraceptives.

*For two out of three regions which contain absolute monarchies, absolute monarchies have relatively low contraceptive prevalence.

*For Western Europe, however, we see that absolute monarchies are the best performing system of government.

##Tab 2: Median Age
*Average population median age by region (x-axis) and system of government (color)

*Western European countries with absolute monarchies have the highest average population median age.

##Tab3: Median Age vs. Contraceptive Prevalence
*Contraceptive prevalence (x-axis) and median age (y-axis)

*Linear model equation is Median Age = 0.179 x (contraceptive prevalence) + 15.647 with the r-squared around a 0.4, the p-value < 0.0001

*One argument against the model is that populations that have low contraceptive prevalence would have more children, and that would lower the median age.


```{r}
inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("LATIN AMER. & CARIB",
"WESTERN EUROPE",
"ASIA (EX. NEAR EAST)",
"SUB-SAHARAN AFRICA",
"NORTHERN AMERICA",
"NEAR EAST",
"NORTHERN AFRICA",
"EASTERN EUROPE")),
  sliderInput("ContraFilter", label = "Average Contraceptive Prevalence:",
              min = 0, max = 100, value = c(0, 100), step = 10),
  sliderInput("AgeFilter", label = "Median Age:",
              min = 0, max = 60, value = c(0, 60), step = 5)
)
```



```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Contraceptive Bar Chart", tabName = "barchart", icon = icon("dashboard")),
      menuItem("Age Bar Chart", tabName = "barchart2", icon = icon("dashboard")),
      menuItem("Both Scatter Plot", tabName = "scatter1", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "BarChart2"
      tabItem(tabName = "barchart",
        p("This is a barchart of Region and Contraceptive Prevalence"),
        source("jeffbarChart1UI.R",local = TRUE)$value
      ),
       # 2. "BarChart1"
      tabItem(tabName = "barchart2",
        p("This is a barchart of Region and Median Age"),
        source("jeffbarChart2UI.R",local = TRUE)$value
      ),
       # 2. "Scatter1"
      tabItem(tabName = "scatter1",
        p("This is a scatter plot of contraceptive prevalence and Median Age with a linear model equation of Median Age =.179*(contraceptive prevalence) + 15.647"),
        source("jeffScatterPlot1UI.R",local = TRUE)$value
      )
    )
  )
)
source("jeffbarChart1Server.R", local = TRUE)
source("jeffbarChart2Server.R", local = TRUE)
source("jeffScatterPlot1Server.R", local = TRUE)

```

##Embedded Tableau Plot: Contraceptive Prevalence, Literacy Rates, and Median Age
*Contraceptive prevalence on the left axis and literacy rate on the right axis with various median ages along the bottom axis

*Pattern slightly upward sloping

<iframe src="https://public.tableau.com/views/finaltest_10/Sheet4?:showVizHome=no"width="1000" height="800"></iframe>






```{r}
source("derekDataA.R", local = TRUE)
source("derekDataB.R", local = TRUE)
source("derekDataC.R", local = TRUE)
source("derekDataD.R", local = TRUE)
```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
places <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
areas <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
abodes <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
Regions <- eventReactive(c(input$selectRegion_1derek), { 
  library('stringr')
  str_c(input$selectRegion_1derek, collapse=', ')
})
```

```{r}
Reg <- eventReactive(c(input$selectReg_1), { 
  library('stringr')
  str_c(input$selectReg_1, collapse=', ')
})
```

```{r}
Re <- eventReactive(c(input$selectRegi_1), { 
  library('stringr')
  str_c(input$selectRegi_1, collapse=', ')
})
```

```{r}
Re <- eventReactive(c(input$selectRegion_1Orji), { 
  library('stringr')
  str_c(input$selectRegion_1Orji, collapse=', ')
})
```

#Dashboard 3: Exploring Age Distribution, Income, and Technology

According to The Fund for Peace and Foreign Policy, population proportion under 15 years of age is a measure that can serve as an indication of a failed state. In this dashboard we explore this metric, as well as metrics related to national income and technology.

##Tab 1: Population Proportion under 15 Years
*Population proportion under 15 years of age

*It can be observed that Sub-Saharan African countries constitute a notably large portion of countries with over 25% of their population under 15 years of age

*While this is interesting it is not unexpected. An analysis of related metrics such as age dependency ratio (DR), gross national income per capita, and patents granted will yield more insightful news 


##Tab 2: Age Dependency Ratio
*Age dependency ratio (ADR) is an indicator calculated by summing he population under 15 years of age with the population over 65 years of age, and then dividing this sum by the population between ages 15 and 64 (the productive age group)

*ADR essentially communicates the number of dependents that each productive member of society must provide for

*The ADR bar chart in the second tab shows that on average Sub-Saharan African and Western European countries have very high ADR's 

*A high ADR means that a small portion of a country's population is contributing to the economic output, each citizen of productive age carries the burden of many dependents
 

##Tab 3: Gross National Income per Capita
*Gross national income per capita is a country's total income in a year divided by its population, giving the average income of citizens in a country

*For Sub-Saharan African countries, the low results for gross national income per capita go hand in hand with their high ADR's

*With high ADR, total national income is being allocated over a large number of unproductive citizens, thus yielding a lower gross national income per capita

*Surprisingly, although Western European countries recorded the second highest DR ratio, they also had the second highest gross national income per capita

##Tab 4: Average Number of Patents per Region
*The average number of patents per region is being used as an indication of the pervasiveness of technology and innovation in a region 

*Regions that are technologically advanced tend to have high economic output, thus negating the detriments of a high ADR

*Notice that Sub-Saharan African countries feature the lowest amount of patents granted, while Western European countries feature the second highest amount of patents granted 


```{r}
inputPanel(
  selectInput("selectRegion_1derek", label = "Select Region for Population Proportion Under 15 years",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
  sliderInput("PopFilter_1", label = "Population Proportion Under 15:", min = 0, max = 100, value = c(0, 100), step = 1),
  selectInput("selectRegi_1", label = "Select Region for Age Dependency Ratio",choices = places, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA"))
)
```

```{r}
inputPanel(
  selectInput("selectReg_1", label = "Select Region for Gross National Income",choices = areas, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("incomeFilter_1", label = "Gross National Income Per Capita:", min = 0, max = 60870, value = c(0, 60870), step = 100)
)
```

```{r}
inputPanel(
  selectInput("selectRegion_1Orji", label = "Select Region for Average Number of Patents",choices = abodes, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("PatentFilter_1", label = "Average Number of Patents:", min = 0, max = 60095, value = c(0, 60095), step = 100)
)
```



```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Population Proportion Under 15", tabName = "Histo1", icon = icon("dashboard")),
      menuItem("Age Dependency Ratio Barchart", tabName = "barchart1", icon = icon("dashboard")),
      menuItem("Gross National Income per Capita", tabName = "boxplot", icon = icon("dashboard")),
      menuItem("Avg # of Patents per Region", tabName = "brchart2", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Population Proportion Under 15 years Histogram" tab content
      tabItem(tabName = "Histo1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("derekBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Dependent Ratio Barchart" tab content
      tabItem(tabName = "barchart1",
        p("And here."),
        source("derekbarChart2UI.R",local = TRUE)$value
        ),
      # 3. "Gross National Income per Capita Boxplot" tab content
      tabItem(tabName = "boxplot",
        p("And here."),
        source("derekBoxPlot2UI.R",local = TRUE)$value
        ),
      # 4. "Average Number of Patents" tab content
      tabItem(tabName = "brchart2",
        p("And here."),
        source("derekBARUI.R",local = TRUE)$value
        )
      )
    )
  )


source("derekBoxPlot1Server.R", local = TRUE)
source("derekbarChart2Server.R", local = TRUE)
source("derekBoxPlot2Server.R", local = TRUE)
source("derekBARServer.R", local = TRUE)
```




#Embedded Tableau Insights

##Insight 1 - Exploring the Number of Children per Women

*Tableau Story to explore the correlations and variance of the average number of children per women 

*Makes use of maps, tableau actions, and a set

TAB 1
*Scatterplot: shows the negative correlation between the literacy rate and average number of children per woman. Unsurprising, statistically significant, and high R^2, but we want to analyze the residuals.

*Map: Color coded by residuals, blue countries have high residual i.e. more children than predicted by model. Some geographic trends (West Europe and East Asia) but not much. 

*Residuals further explored in tab 2 where we seek correlations 

*Side note: By using the set we can observe that although there is a significant model for the aggregate of all countries, when we filter to the just the 20 wealthiest countries (by average income per capita) there is not a significant model

TAB 2
*We compare residuals to other measures: infant mortality rate on the left, population proportion over 0 on the right. 

*Both correlations were significant but have fairly weak correlation coefficients

*This was particularly surprising for the right plot because we expected to see populations which tend to be older have less children than expected, but a weak correlation coefficients indicates this isn't really the case.

<iframe src="https://public.tableau.com/views/final_project_brandon_insight/ChildrenPerWomenStory?:showVizHome=no"width="1416" height="814"></iframe>


##Insight 2 - Income per Capita vs Region
*By arranging this boxplot with x-axis as region and y-axis as gross national income, we see that sub-Saharan African countries have the lowest level of incomes, and that the higher outliers are republics.

<iframe src="https://public.tableau.com/views/AnalysisofWHOdata/Sheet2?:showVizHome=no"width="1050" height="814"></iframe>

##Insight 3 - Income per Capita vs System of Government
*By arranging this boxplot with x-axis as system of government and y-value as gross national income with region as color, we can observe that constitutional monarchies in general have a high percentage of countries in the lower quartiles compared to republics

<iframe src="https://public.tableau.com/views/AnalysisofWHOdata/Sheet1?:showVizHome=no"width="1050" height="814"></iframe>

##Insights 4-6 - Health Metrics compared across System of Government
*It can be seen that by examining the quality of life indicators of constitutional monarchies such as infant mortality rate, per capita government expenditure on health and contraceptive prevalence that sub-Saharan constitutional monarchies have a lower quality of life than other forms of government on average

<iframe src="https://public.tableau.com/views/AnalysisofWHOdata/Sheet7?:showVizHome=no"width="1050" height="814"></iframe>

<iframe src="https://public.tableau.com/views/AnalysisofWHOdata/Sheet8?:showVizHome=no"width="1050" height="814"></iframe>

<iframe src="https://public.tableau.com/views/AnalysisofWHOdata/Sheet9?:showVizHome=no"width="1050" height="814"></iframe>

#Conclusion

Highlighting some of the key takeaways:

*Spending more money on healthcare to give the population greater access to contraceptives appears to work well for Absolute Monarchies and Republics, but for Constitutional Monarchies the individual income and region have a stronger correlation.

*Although we tend to think of Republics as giving the most economic and social freedom, they do not always have the strongest access to contraceptive - it depends on the education. 

*Regions with higher dependency ratios do not always have a lower income per capita, how technologically advanced a region is also a key factor (e.g. Europe vs Africa both having a high ratio but different incomes per capita).

*The relationship between number and children and education is clear, but the variance is best explained by quite a few factors put together (e.g. region, infant mortality rate) rather than just one factor.

*System of government does have a bearing on health metrics / quality of life, but there is also a dependence on the region.

#Appendix 

##Data Cleaning Code
(Click "code" to your right to see the code)
```{r, eval= FALSE}
library(tidyverse)
csvURL <- "https://query.data.world/s/8NFAXz99XN1E_ZYGRuRCCL7d751DpX"
df <- read_csv(csvURL, col_types = list(
  country = col_character(),
 
  adult_literacy_rate = col_number(), #changed to numbers
  gross_national_income_per_capita_ppp_international = col_number(), 
  population_in_thousands_total = col_number(), 
  population_median_age_years = col_number(),
  per_capita_total_expenditure_on_health_ppp_int = col_number(),
  per_capita_government_expenditure_on_health_ppp_int = col_number(),
  healthy_life_expectancy_hale_at_birth_years_both_sexes = col_number(),
  life_expectancy_at_birth_years_both_sexes =col_number(),
  population_with_sustainable_access_to_improved_sanitation_total = col_number(),
  aid_received_total = col_number(),
  income_per_person= col_number(),
  population_proportion_over_60= col_number(),
  population_proportion_under_15= col_number(),
  contraceptive_prevalence= col_number(),
  total_expenditure_on_health_as_percentage_of_gross_domestic_product= col_number(),
  children_per_woman= col_number(),
  infant_mortality_rate= col_number(),
  patents_granted= col_number()
  
))
  



# Remove non-printable characters from column names.
names(df) <- gsub("[^ -~]", "", names(df)) 
names(df) <- gsub(" ", "_", names(df)) 
#Get rid of null values
df[is.na(df)] <-0


# Remove non-printable characters from all column values.
df <- df %>% dplyr::mutate_all(funs(gsub(pattern="[^ -~]", replacement= "", .)))

# The following write_csv followed immediately by a read_csv, fixes the column types.
write_csv(df, "/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv") 

df <- read_csv("/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv", col_types = list(
  country = col_character(),
  
  adult_literacy_rate = col_number(), #changed to numbers
  gross_national_income_per_capita_ppp_international = col_number(), 
  population_in_thousands_total = col_number(), 
  population_median_age_years = col_number(),
  per_capita_total_expenditure_on_health_ppp_int = col_number(),
  per_capita_government_expenditure_on_health_ppp_int = col_number(),
  healthy_life_expectancy_hale_at_birth_years_both_sexes = col_number(),
  life_expectancy_at_birth_years_both_sexes =col_number(),
  population_with_sustainable_access_to_improved_sanitation_total = col_number(),
  aid_received_total = col_number(),
  income_per_person= col_number(),
  population_proportion_over_60= col_number(),
  population_proportion_under_15= col_number(),
  contraceptive_prevalence= col_number(),
  total_expenditure_on_health_as_percentage_of_gross_domestic_product= col_number(),
  children_per_woman= col_number(),
  infant_mortality_rate= col_number(),
  patents_granted= col_number()
))
# Now save the cleaned data to new.csv
write_csv(df, "/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv")


# Now load /tmp/new.csv into a data.world Dataset.
```

##SessionInfo

```{r}
sessionInfo()
```
