---
title: "The Health of Countries: An Interactive Document"
author: "Kyle DeQuesnay, Jeffrey Feng,Brandon Kerbow, Derek Orji"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---

#Dataset Description
This dataset was obtained online from the World Health Organization (WHO) and contains various health-related metrics for every country on the planet. Examples of such metrics include the average per capita (per person) income and average life expectancy. There are also fields for the region (e.g. Western Europe, Sub-Saharan Africa) and the system of government in place (e.g. Republic, Absolute Monarchy) for each country.

#Important Links

[Data.world Project](https://data.world/jeffrey-feng/s18-edv-project-3)

Kyle's Insights: [1](https://data.world/jeffrey-feng/s18-edv-project-3/insights/3f4ad123-96f8-43ef-a9bd-6e7707b5894e)
[2](https://data.world/jeffrey-feng/s18-edv-project-3/insights/4bf66d41-46db-46bf-95d6-0fd1f5415b53)

Jeffrey's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-3/insights/6c074812-db39-4d90-9267-98a018e0d205)
[2](https://data.world/jeffrey-feng/s18-edv-project-3/insights/406defbc-4867-4f7a-b9f7-0ededdfec75b)

Brandon's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-3/insights/c768d907-2631-4ab8-a277-01971367da4e)
[2](https://data.world/jeffrey-feng/s18-edv-project-3/insights/2c8243ec-112e-4eae-84b9-1737eecc4c22)
[3](https://data.world/jeffrey-feng/s18-edv-project-3/insights/55d632d3-9c26-47a8-8ad8-1c810833f5f8)

Derek's Insights:
[1](https://data.world/jeffrey-feng/s18-edv-project-3/insights/7eeb0512-fd4d-4e2c-89ab-8ee605bc6123)
[2](https://data.world/jeffrey-feng/s18-edv-project-3/insights/9afba264-eeac-40ea-9e5b-bedd70555b83)

[Github Repository](https://github.com/CannataUTDV/s18dvproject3-duquesnay-feng-orji-kerbow)

#Motivations and Expectations
With healthcare being a hot topic in both business and everyday life, we wanted to explore some drivers for health on a global scale. Because one of the most common obstacles in improving global health is a lack of funds, we aimed to explore how countries - of different government types and in different geographic regions - can benefit from increasing the amount they spend on healthcare. We also recognize that in many countries, particularly 3rd world countries, it is common for women to give birth to a relatively high number of children. With this in mind, we explored what factors could affect the prevalence of contraception (in other words, the accessibility of birth control such as condoms or pills). We also wanted to explore the overall health of countries by analyzing demographics/age distributions and the potential relationships with factors such as income. As an interesting final point of interest, we wanted to see if there is a relationship between climate (approximated by average annual temperature) and average number of women per children. 

We expect to see that countries which spend more on healthcare have better health (measured by things such as life expectancy) for every region and system of government. We also expect to see that women in poorer nations give birth to more children and that countries with aging populating are not as healthy as their middle-aged country counterparts. Finally, we expect there to be little correlation between climate and the average number of children per woman. More specific expectations are in the sections for each dashboard further down in this interactive document. 

#Summary of Conclusions
Through our analysis of the data and visuals in subsequent sections, we found that our expectations were not always correct. Although it is true that that countries which spend more on healthcare tend to have better health-related metrics, the relationship does not always hold for all metrics and systems and government. Additionally, what plays into the prevalence of contraceptive is more than just average income and aging populations are not necessarily unhealthier than their middle-aged country counterparts. Lastly, we did observe a pattern in climate vs average number of children per woman: as average temperature rose, so did the number of children. More specific conclusions for each dashboard can be found in each dashboards corresponding text. 


```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(shiny)
library(grid)
library(data.world)
library(DT)
library(shinydashboard)
library(plotly)
library(lubridate)
library(leaflet)
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
source("brandonsDataA.R", local = TRUE)
source("brandonsDataB.R", local = TRUE)
source("brandonsDataC.R", local = TRUE)
source("brandonsDataD.R", local = TRUE)
source("brandonsDataE.R", local = TRUE)
```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
systemsOfGovernment <- data.world::query(data.world::qry_sql(
 "   
	select distinct system_of_government from who_cleanest

 "), 
dataset = project)
```


```{r}
SystemsOfGovernment  <- eventReactive(c(input$selectSystemOfGovernment_1), { 
  library('stringr')
  str_c(input$selectSystemOfGovernment_1, collapse=', ')
})
```

#Dashboard 1 - Benefits of Spending on Healthcare
One important question surrounding the issue of global health is how much money countries should spend on improving it. The three scatterplot tabs in the dashboard below explore answers that question. To see what kind of returns countries can attain from spending, we focus on relationships between healthcare expenditure (% of GDP, with GDP being the total value of goods produced annually within a country) vs common health metrics such as life expectancy and contraceptive prevalence. Contraceptive prevalence is the percent of the population which has access to readily available contraception. Contraception is any tool for preventing pregnancy and includes condoms and birth control pills. Because the system of government can have a large effect on how far money can go in improving the health of a country, the plots are colored by system of government. We would expect that for any given system of government, an increase in spending tends to improve common health metrics. As you will see in our analysis, however, this is not always the case.

The input panel allows the user to decide which system(s) of government they would like to see present in the data. It is advised to exclude "n/a" because this means the country did not have a system of government listed in the dataset. Note that for these plots, and some others on this document, the text in the legend is quite small. This is to avoid having the legend overlay the plot. 

##Tab 1 - Life Expectancy
The first tab's scatterplot shows the relationship between health expenditure as % of GDP (x-axis) and life expectancy (y-axis). Each dot represents a country and each line shows the linear fit for a given system of government. The interactive legend to the right of the plot shows which color dot corresponds to which country, and which color line corresponds to which system of government. Note that you must scroll down to the bottom of the legend to see which color line corresponds to which system of government. In this visual there is a clear positive trend for each system of government, which is unsurprising. But is there always a relationship between spending and common health metrics? We explore this further in the next tab's visual.

##Tab 2 - Contraceptive Prevalence
The second tab's scatterplot shows the relationship between health expenditure as % of GDP (x-axis) and contraceptive prevalence (y-axis). Once again we have the dots and lines corresponding to country and system of government, respectively. On this plot it is interesting to observe that for constitutional monarchies, there does not appear to be an increase in contraceptive prevalence that comes with an increasing in spending. This is counter intuitive and begs the question: what factors DO affect the contraceptive prevalence in constitutional monarchies? We explore this in the next tab's visual. 

##Tab 3 - Average Income
The third tab's visual shows the relationship between average income per capita/person (x-axis) and contraceptive prevalence (y-axis). Once again we have the dots and lines corresponding to countries and systems of government, respectively. We can observe a correlation between these two fields for all three system of governments, but the correlation is strongest for the constitutional monarchies. This - combined with the second visual - implies that in constitutional monarchies, individual income is a larger factor in contraceptive prevalence than the country's overall healthcare expenditure. 

```{r}
inputPanel(
  selectInput("selectSystemOfGovernment_1", label = "Select System of Government",choices = systemsOfGovernment , multiple=TRUE, selected=c("Absolute_monarchy", "Republic", "Constitutional_monarchy"))
)
```



```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Life Expectancy vs Health Expenditures", tabName = "scatter0", icon = icon("dashboard")),
      
      menuItem("Contraceptive Prevalence vs Health Expenditures", tabName = "scatter", icon = icon("dashboard")), 
      
      menuItem("Contraceptive Prevalence vs Income per Person", tabName = "scatter2", icon = icon("dashboard")),
      
      menuItem("Average Residual by Region", tabName = "brandonboxplot1", icon = icon("dashboard")),
      
       menuItem("Contraceptive Prevalence vs Income per Person for Constitutional Monarchies", tabName = "scatter3", icon = icon("dashboard"))
      
    )
  ),
  dashboardBody(
    tabItems(
      # 0. "Life Expectancy vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter0",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("brandonsScatterPlot0UI.R",local = TRUE)$value
      ),
        
        
      # 1. "Contraceptive Prevalence vs Health Expenditures (% of GDP) Scatter Plot" tab content
      tabItem(tabName = "scatter",
        p("Absolute Monarchies (orange line) ~ P-value: 0.0026, R^2: 0.97..............................................        
           Republics (purple line) ~ P-value: 0.00013, R^2: 0.121 ..............................................................
            Constitutional Monarchies (dark green line) ~ P-value: 0.93, R^2: 0.0004.................................."),
        source("brandonsScatterPlot1UI.R",local = TRUE)$value
      ),
      
      # 2. "Contraceptive Prevalence vs Income per Person Scatter Plot" tab content
      tabItem(tabName = "scatter2",
        p("Absolute Monarchies (orange line) ~ P-value: 0.82, R^2: 0.074..............................................        
           Republics (purple line) ~ P-value: 0.0001, R^2: 0.204 ..............................................................
            Constitutional Monarchies (dark green line) ~ P-value: 0.012, R^2: 0.35.................................."),
        source("brandonsScatterPlot2UI.R",local = TRUE)$value
      ), 
      
      # 3. "Average residual by Region" tab content
      tabItem(tabName = "brandonboxplot1",
        p("Filter to show only Constitutional Monarchies"),
        source("brandonBarChart1UI.R",local = TRUE)$value
      ),
      
      # 3. "income vs constraceptive prevalence for constitutional monarchies" tab content
      tabItem(tabName = "scatter3",
        p("East Asia (brown line) ~ P-value: 0.09,   R^2: 0.98..................................................................................   
           Sub-Saharan Africa (purple line) ~ P-value: 0.031,   R^2: 0.64 .............................................................
            C.W. of Ind States (dark green line) ~ P-value: 0.13,   R^2: 0.57............................................................"),
        source("brandonsScatterPlot3UI.R",local = TRUE)$value
      )
      
    )
  )
)

source("brandonsScatterPlot0Server.R", local = TRUE)
source("brandonsScatterPlot1Server.R", local = TRUE)
source("brandonsScatterPlot2Server.R", local = TRUE)
source("brandonbarChart1Server.R", local = TRUE)
source("brandonsScatterPlot3Server.R", local = TRUE)
```



```{r}
source("jeffDataA.R", local = TRUE)
source("jeffDataB.R", local = TRUE)

```


```{r}
projectJeff <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from WHO_Cleanest
 "), 
dataset = projectJeff)
```

#Dashboard 2 - Contraceptive Prevelance

A similar topic of interest is whether or not the system of government or region has a bearing on the contraceptive prevalence. Answers to this question are explored in the dashboard below. This dashboard contains two tabs, both bar charts. The input panel controls the regions of the world which are shown and the top and bottom sliders control the range of y-values for the bar charts in the first and second tab, respectively. 

##Tab 1: By Region and Government
The first bar chart shows the average contraceptive prevalence (y-axis) by both region (x-axis) and system of government (color). One might expect that countries which are republics have the best access to contraceptives since republics tend to have more freedom in their economies, but we observe that this is actually not always the case. For two out of three regions which contain absolute monarchies, absolute monarchies perform poorly (low contraceptive prevalence) relative to other systems of government. For Western Europe, however, we see that absolute monarchies are the best performing system of government. To explore why this may be the case, we can observe the second tab's bar chart.

##Tab 2: Median Age
This bar chart shows the average population median age by region (x-axis) and system of government (color). It can be observed from this plot that out of those three regions with absolute monarchies, Western European countries with absolute monarchies have the highest average population median age. The higher median age of these countries could explain the higher access to contraceptives, as older people tend to be wiser and therefore likely to be familiar with the avenues of obtaining contraceptives.


```{r}
inputPanel(
  selectInput("selectRegion_1", label = "Select Region",choices = regions, multiple=TRUE, selected=c("LATIN AMER. & CARIB",
"WESTERN EUROPE",
"ASIA (EX. NEAR EAST)",
"SUB-SAHARAN AFRICA",
"NORTHERN AMERICA",
"NEAR EAST",
"NORTHERN AFRICA",
"EASTERN EUROPE")),

  sliderInput("ContraFilter", label = "Average Contraceptive Prevalence:",
              min = 0, max = 100, value = c(0, 100), step = 10),
sliderInput("AgeFilter", label = "Average Median Age:",
              min = 0, max = 80, value = c(0, 80), step = 10)
)
```




```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Contraceptive Bar Chart", tabName = "barchartJeff", icon = icon("dashboard")),
      menuItem("Age Bar Chart", tabName = "barchart2Jeff", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "BarChart2"
      tabItem(tabName = "barchartJeff",
        p("This is a barchart of Region and Contraceptive Prevalence"),
        source("jeffbarChart1UI.R",local = TRUE)$value
      ),
       # 2. "BarChart1"
      tabItem(tabName = "barchart2Jeff",
        p("This is a barchart of Region and Median Age"),
        source("jeffbarChart2UI.R",local = TRUE)$value
      )
    )
  )
)
source("jeffbarChart1Server.R", local = TRUE)
source("jeffbarChart2Server.R", local = TRUE)

```



```{r}
source("derekDataA.R", local = TRUE)
source("derekDataB.R", local = TRUE)
source("derekDataC.R", local = TRUE)
```


```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
places <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3" 
data.world::set_config(cfg_env("DW_API")) 
areas <- data.world::query(data.world::qry_sql(
 "   
	select distinct region
	from who_cleaner

 "), 
dataset = project)
```


```{r}
Regions <- eventReactive(c(input$selectRegion_1derek), { 
  library('stringr')
  str_c(input$selectRegion_1derek, collapse=', ')
})
```

```{r}
Reg <- eventReactive(c(input$selectReg_1), { 
  library('stringr')
  str_c(input$selectReg_1, collapse=', ')
})
```

```{r}
Re <- eventReactive(c(input$selectRegi_1), { 
  library('stringr')
  str_c(input$selectRegi_1, collapse=', ')
})
```


#Dashboard 3: Exploring Age and Income

According to The Fund for Peace and Foreign Policy, population proportion under 15 years of age is a measure that can serve as an indication of a failed state. In this dashboard we explore this metric, how it varies by region, and potential causes for the metric being high or low. The input panel controls the regions which are shown for each visual. The top and bottom sliders control the range of y values on tabs one and three, respectively. 

##Tab 1: Population Proportion under 15 Years
The histogram in this dashboard's first tab shows the population proportion under 15 for each region, represented by different colors. In looking at this data across the different regions, it can be observed that Sub-Saharan African countries constitute a notably large portion of countries with over 25% of their population under 15 years of age. This is interesting but not unexpected. 

To further dig into this metric, we will explore what factors may affect the population proportion under 15 years. The selected factors are age dependency ratio (DR) and gross national income per capita. These are examined in the next two plots.

##Tab 2: Age Dependency Ratio
Age dependency ratio (DR) is an indicator calculated by summing he population under 15 years of age with the population over 65 years of age, and then dividing this sum by the population between ages 15 and 64 (the productive age group). DR essentially communicates the number of dependents that each a productive member of society must provide for. It has many implications for the performance of national economies. The age dependency ratio bar chart in the second tab shows that on average Sub-Saharan African countries have very high DR ratios. Sub-Saharan African countries displayed an average DR ratio of 0.89, much higher than the next highest ratio of 0.62  held by Western European countries. The fact that a region so underdeveloped has such a small amount of their population contributing to their national economy does not bode well for them. In short, a high DR ratio means that a small portion of a country's population is contributing to the economic output, and each member of productive age carries the burden many dependents. To explore factors which could explain these DR values we observe the average income per capita for these regions in the next tab.
 

##Tab 3: Gross National Income per Capita
This tab is a series of boxplots which show, for each Region (x-axis and color), the distribution of gross national income per capita for every country within that region. Gross national income per capita is a country's total income in a year divided by its population, giving the average income of citizens in a country. For Sub-Saharan African countries, the low results for gross national income per capita were not surprising. This observation goes hand in hand with their low DR ratio: with such a small portion of their population producing economically, the total national income is being allocated over a large number of unproductive citizens, thus yielding a lower gross national income per capita. The boxplot for Sub-Saharan African countries has a number of outliers which appear to be from countries that have recently been adopting technology (e.g. Botswana) or have a stable tourism industry (e.g. Seychelles). 

Surprisingly, although Western European countries recorded the second highest DR ratio, they also had the second highest gross national income per capita. This is striking as it would be expected that they suffer the difficulties of having such a large portion of unproductive citizens. The key to this is in realizing that Western European countries are amongst the most technologically, economically, and socially advanced - especially under western criteria. Because of this, the relatively small portion of productive people in the region can produce economic output that surpasses that of other regions. The same cannot be said for the still developing Sub-Saharan African countries. This is explored further in the next dashboard.


```{r}
inputPanel(
  selectInput("selectRegion_1derek", label = "Select Region for Population Proportion Under 15 years",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
  sliderInput("PopFilter_1", label = "Population Proportion Under 15:", min = 0, max = 100, value = c(0, 100), step = 1),
  selectInput("selectRegi_1", label = "Select Region for Age Dependency Ratio",choices = places, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA"))
)
```

```{r}
inputPanel(
  selectInput("selectReg_1", label = "Select Region for Gross National Income",choices = areas, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "OCEANIA", "LATIN AMER. & CARIB", "NEAR EAST", "ASIA (EX. NEAR EAST)", "C.W. OF IND. STATES", "EASTERN EUROPE", "NORTHERN AFRICA", "WESTERN EUROPE", "BALTICS", "NORTHERN AMERICA")),
 sliderInput("incomeFilter_1", label = "Gross National Income Per Capita:", min = 0, max = 60870, value = c(0, 60870), step = 100)
)
```



```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Population Proportion Under 15 years Histogram", tabName = "Histo1", icon = icon("dashboard")),
      menuItem("Age Dependency Ratio Barchart", tabName = "barchart1", icon = icon("dashboard")),
      menuItem("Gross National Income per Capita Boxplot", tabName = "boxplot", icon = icon("dashboard"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Population Proportion Under 15 years Histogram" tab content
      tabItem(tabName = "Histo1",
        p("You can actually put some descriptive text here - see https://shiny.rstudio.com/articles/css.html"),
        source("derekBoxPlot1UI.R",local = TRUE)$value
      ),
      # 2. "Dependent Ratio Barchart" tab content
      tabItem(tabName = "barchart1",
        p("And here."),
        source("derekbarChart2UI.R",local = TRUE)$value
        ),
      # 3. "Gross National Income per Capita Boxplot" tab content
      tabItem(tabName = "boxplot",
        p("And here."),
        source("derekBoxPlot2UI.R",local = TRUE)$value
        )
      )
    )
  )


source("derekBoxPlot1Server.R", local = TRUE)
source("derekbarChart2Server.R", local = TRUE)
source("derekBoxPlot2Server.R", local = TRUE)
```





```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
data.world::set_config(cfg_env("DW_API")) 
regions <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.region from WHO_Cleanest
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
data.world::set_config(cfg_env("DW_API")) 
incomes <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.gross_national_income_per_capita_ppp_international
  from WHO_Cleanest
  "), 
  dataset = project)
```

```{r}
project <- "https://data.world/jeffrey-feng/s18-edv-project-3/"  
data.world::set_config(cfg_env("DW_API")) 
system <- data.world::query(data.world::qry_sql(
  "   
  select distinct WHO_Cleanest.system_of_government from WHO_Cleanest
  "), 
  dataset = project)
```



```{r}

df1kyle <- eventReactive(c(input$selectIncome_1kyle, input$selectRegion_1kyle), { 
  project <- "https://data.world/jeffrey-feng/s18-edv-project-3/" 
  data.world::set_config(cfg_env("DW_API")) 
  paramQuery <- data.world::qry_sql(
    "   
    select region, gross_national_income_per_capita_ppp_international, system_of_government
    from WHO_Cleanest h
    where gross_national_income_per_capita_ppp_international between ? and ? and region in (?,?,?,?,?,?,?,?,?,?) and system_of_government in ('Republic','Constitutional_monarchy', 'Absolute_monarchy')
    
    order by region
    ")
  paramQuery$params <- c(input$selectIncome_1kyle[1], input$selectIncome_1kyle[2], input$selectRegion_1kyle[1], input$selectRegion_1kyle[2], input$selectRegion_1kyle[3], input$selectRegion_1kyle[4], input$selectRegion_1kyle[5], input$selectRegion_1kyle[6], input$selectRegion_1kyle[7], input$selectRegion_1kyle[8], input$selectRegion_1kyle[9], input$selectRegion_1kyle[10])
  data.world::query(paramQuery, dataset = project)
}) 

```








```{r}
Region <- eventReactive(c(input$selectRegion_1kyle), { 
  library('stringr')
  str_c(input$selectRegion_1kyle, collapse=', ')
})
```


```{r}
Income <- eventReactive(c(input$selectIncome_1kyle), { 
  library('stringr')
  str_c(input$selectIncome_1kyle, collapse=', ')
})
```

#Dashboard 4 - Further Insight on Income
This dashboard shows a boxplot comparing gross income per capita (y-axis) across regions (x-axis). This visual expands on the third tab in the previous dashboard by color-coding based on system of government. The input panel filters the regions shown. The slider adjuts the range of the y values.

To expand on an observation made in tab three of the previous dashboard, we notice that Sub-Saharan Africa has the highest amount of outliers. From this visual we gain some insight into what may be causing this: all of these outlier countries are republics. This trend seems to imply a higher chance of a Sub-Saharan country having a higher income per capita if it is a republic, as republics in Africa have a much higher average income per capita than the other systems of government present there.


```{r}
inputPanel(
  selectInput("selectRegion_1kyle", label = "Select Regions",choices = regions, multiple=TRUE, selected=c("SUB-SAHARAN AFRICA", "BALTICS", "OCEANIA", "C.W.OF IND.STATES", "WESTERN EUROPE", "LATIN AMER. & CARIB", "ASIA (EX. NEAR EAST)", "EASTERN EUROPE", "NEAR EAST", "NORTHERN AFRICA")
    
  )
  
  ,sliderInput("selectIncome_1kyle", label = "Gross national income per capita:", min = 0, max = 61000, value = c(0, 61000), step = 100)
)
```

```{r}
dashboardPage(
  dashboardHeader(
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("proportion of population under 15", tabName = "boxplot1", icon = icon("dashboard1"))
    )
  ),
  dashboardBody(
    tabItems(
      # 1. "Gross national income per capita by region" tab content
      tabItem(tabName = "boxplot1",
              source("kyleBoxPlot1UI.R",local = TRUE)$value
      )
    )
  )
)

source("kyleBoxPlot1Server.R", local = TRUE)

```


#Embedded Tableau Insights

##Insight 1 - Temperature vs Children per Woman

(Note: Tableau's capability to zoom in to maps may prove useful if the maps appear too small).
This embedded Tableau dashboard includes two maps and a scatterplot. The two maps, top and bottom, show average annual temperature and average number of children per woman, respectively, by country and color. Although a correlation is clear from the maps, the children per woman map shows a less vibrant range of colors. This is because countries in Sub-Saharan Africa have such a high number of children per woman that they skew the distribution of colors. One interesting observation is Brazil, having a high average temperature but low average number of children per woman. Searches online indicate that reasons for this may be that Brazil is rapidly modernizing and attaining better education. The scatterplot shows the overall correlation between temperature and children per woman. An interesting observation is that Afghanistan has a higher number of women per children than expected, which is likely due to the culture and lack of education.

Note that the map can act as a filter for the scatterplot. 

<iframe src="https://public.tableau.com/views/project3embedTableauOnR/Dashboard?:showVizHome=no"width="800" height="800"></iframe>




#Appendix 

##Data Cleaning Code
(Click "code" to your right to see the code)
```{r, eval= FALSE}
library(tidyverse)
csvURL <- "https://query.data.world/s/8NFAXz99XN1E_ZYGRuRCCL7d751DpX"
df <- read_csv(csvURL, col_types = list(
  country = col_character(),
 
  adult_literacy_rate = col_number(), #changed to numbers
  gross_national_income_per_capita_ppp_international = col_number(), 
  population_in_thousands_total = col_number(), 
  population_median_age_years = col_number(),
  per_capita_total_expenditure_on_health_ppp_int = col_number(),
  per_capita_government_expenditure_on_health_ppp_int = col_number(),
  healthy_life_expectancy_hale_at_birth_years_both_sexes = col_number(),
  life_expectancy_at_birth_years_both_sexes =col_number(),
  population_with_sustainable_access_to_improved_sanitation_total = col_number(),
  aid_received_total = col_number(),
  income_per_person= col_number(),
  population_proportion_over_60= col_number(),
  population_proportion_under_15= col_number(),
  contraceptive_prevalence= col_number(),
  total_expenditure_on_health_as_percentage_of_gross_domestic_product= col_number(),
  children_per_woman= col_number(),
  infant_mortality_rate= col_number(),
  patents_granted= col_number()
  
))
  



# Remove non-printable characters from column names.
names(df) <- gsub("[^ -~]", "", names(df)) 
names(df) <- gsub(" ", "_", names(df)) 
#Get rid of null values
df[is.na(df)] <-0


# Remove non-printable characters from all column values.
df <- df %>% dplyr::mutate_all(funs(gsub(pattern="[^ -~]", replacement= "", .)))

# The following write_csv followed immediately by a read_csv, fixes the column types.
write_csv(df, "/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv") 

df <- read_csv("/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv", col_types = list(
  country = col_character(),
  
  adult_literacy_rate = col_number(), #changed to numbers
  gross_national_income_per_capita_ppp_international = col_number(), 
  population_in_thousands_total = col_number(), 
  population_median_age_years = col_number(),
  per_capita_total_expenditure_on_health_ppp_int = col_number(),
  per_capita_government_expenditure_on_health_ppp_int = col_number(),
  healthy_life_expectancy_hale_at_birth_years_both_sexes = col_number(),
  life_expectancy_at_birth_years_both_sexes =col_number(),
  population_with_sustainable_access_to_improved_sanitation_total = col_number(),
  aid_received_total = col_number(),
  income_per_person= col_number(),
  population_proportion_over_60= col_number(),
  population_proportion_under_15= col_number(),
  contraceptive_prevalence= col_number(),
  total_expenditure_on_health_as_percentage_of_gross_domestic_product= col_number(),
  children_per_woman= col_number(),
  infant_mortality_rate= col_number(),
  patents_granted= col_number()
))
# Now save the cleaned data to new.csv
write_csv(df, "/Users/Jeffrey/Documents/school/Spring 2018/cs329/proj1/CS329DataViz/Project_3/WHO_clean.csv")


# Now load /tmp/new.csv into a data.world Dataset.
```

##SessionInfo

```{r}
sessionInfo()
```
